---
title: "AI Classifier"
output: null
date: 8-20-2026
---

```{r}
#install.packages("ellmer")
library(ellmer)
library(tidyverse)
library(glue)
library(janitor)
library(purrr)
library(stringr)

Sys.setenv(GOOGLE_API_KEY = "")

```

#Check Gemini is working

```{r}
chat <- chat_google_gemini()

chat$chat("Tell me four jokes about local data journalists")
```

### Load LAT Data
```{r echo = F}
#2501 articles in index
lat_article_index <-  rio::import("https://www.dropbox.com/scl/fi/keibb551rna0cedqxasiu/lat_txt_index_renamed_7_23.csv?rlkey=5avoupjokl8j8xnre11sqxhmb&st=la36umz6&dl=1") |> 
  clean_names() |> 
  mutate(year = lubridate::year(date))


#284067 rows of text
lat_articles_text <-  rio::import("https://www.dropbox.com/scl/fi/etw3pxonox4tijdwr6gmn/moley_lat_text_june_21.csv?rlkey=9h5do6lnkgdy8gx1pyqpz79ui&st=6t73d92b&dl=1") |>
   clean_names() |>
    mutate(year = as.numeric(year)) |> 
  mutate(new_filename = paste0(date,"_",filename))

# lat_articles_text <- experiment
```
### Process LAT data
Collapse article text into single column
```{r}
#tighter
processed_llm <- lat_articles_text %>%
  group_by(filename) %>%
  summarize(
    # Join sentences and clean up line-break hyphens
    full_text = paste(na.omit(sentence), collapse = " ") %>% 
                str_replace_all("- ", "") %>% 
                str_squish(),
    
    # Keep all other metadata columns
    across(everything(), \(x) first(na.omit(x)))
  ) %>%
  ungroup() %>%
  # Filter for your target year
  filter(year >= 1950, year < 1960) %>%
  subset(select = -c(filename, sentence, document_url, pages, issn)) |> 
  # Final safety check: Ensure one row per article
  distinct(new_filename, .keep_all = TRUE) %>%
  # Assign Batch IDs (10 articles per batch)
  mutate(batch_id = ceiling(row_number() / 10))

```



# LLM Prompts


### Politics
Using model = "gemini-2.5-flash".

```{r}
chat_politics <- chat_google_gemini(system_prompt = "You are an academic researcher performing context analysis on selected news articles. Analyze each article and classify it based on specified criteria.

In this prompt, the phrases “category” and “classification” and any of their grammatical variations are synonymous. 

An article should receive a classification if it meets the requirements for the category specified below. Each article must independently meet a threshold of three or more mentions of specified criteria to be included in a specific category.

If an article meets none of the criteria, classify it as 'other'

—-Start Category Criteria—---

POLITICS: an article contains, in text, content, or theme, three or more of the following

- Voting in a political election
- Upcoming elections (primaries, general elections, special elections)
- Election results and outcomes
- Political campaigns
- Political campaign strategies
- Candidate announcements, debates, or endorsements
- Election polling and predictions
- Political party activities related to elections
- Specific words: “election”, “vote”, “polls”, “ballots”, “candidate”


For the above category, there are some topics that could create a classification “gray area”. For the purposes of this research, use the following descriptions to validate classifications.  Any article that any of these apply to can still be categorized as multiple categories.

If the article discusses, in text, theme, or content, policy debates or legislation without electoral context, then it can be marked as 'other', among any other applicable categories
If the article discusses, in text, theme, or content, appointed officials or bureaucratic actions, then it is not ‘politics’ category unless the discussion is tied to an election

—-End Category Criteria—---


Return ONLY a CSV with exactly THREE columns and NO additional text:

Column 1: new_filename (the article identifier)
Column 2: category 
Column 3: explanation (brief justification citing specific counts)

- Include a header row: new_filename,category,explanation
- No quotes around values unless they contain commas
- Multiple categories in alphabetical order separated by semicolons
- Explanation must specify the count for each assigned category
- Maximum 15 words per explanation

Examples:
article1.txt,politics,`3 mentions of election campaigns, 2 candidate endorsements`
No other explanation is required for 'other'."
)

```

### Voter_Turnout

```{r}
chat_voter <- chat_google_gemini(system_prompt =  "You are an academic researcher performing context analysis on selected news articles. Analyze each article and classify it based on specified criteria.

In this prompt, the phrases “category” and “classification” and any of their grammatical variations are synonymous. 

An article should receive a classification if it meets the requirements for the category specified below. Each article must independently meet a threshold of three or more mentions of specified criteria to be included in a specific category.

If an article meets none of the criteria, classify it as 'other'


—-Start Categories Criteria—---

VOTER TURNOUT: an article contains four or more,  in text, content, or theme, mentions of 
Voter registration drives or registration statistics
Efforts to get people to vote in elections
Barriers to voting or voter access issues (accessing polling locations, voter ID requirements, wait times, etc.)
Efforts supress or discourage people from voting in elections



—-End Categories Criteria—---


Return ONLY a CSV with exactly THREE columns and NO additional text:

Column 1: new_filename (the article identifier)
Column 2: category (one or more classifications separated by semicolons)
Column 3: explanation (brief justification citing specific counts)

- Include a header row: new_filename,category,explanation
- No quotes around values unless they contain commas
- Multiple categories in alphabetical order separated by semicolons
- Explanation must specify the count for each assigned category
- Maximum 15 words per explanation

Examples:
article1.txt,voter_turnout,`3 mentions of Voter registration drives, 2 Get-out-the-vote efforts` 

No other explanation is required for 'other'."
)

```

### Economy

```{r}
chat_econ <- chat_google_gemini(system_prompt =  "You are an academic researcher performing context analysis on selected news articles. Analyze each article and classify it based on specified criteria.

In this prompt, the phrases “category” and “classification” and any of their grammatical variations are synonymous. 

An article should receive a classification if it meets the requirements for the category specified below. Each article must independently meet a threshold of three or more mentions of specified criteria to be included in a specific category.

If an article meets none of the criteria, classify it as 'other'


—-Start Categories Criteria—---

ECONOMY:  an article contains three or more,  in text, content, or theme, mentions of 
Macroeconomic issues or economic policy. That would include discussions of the federal debt, the labor market, economic growth or contraction
Macroeconomic indicators (Examples: GDP, inflation, unemployment rates, economic growth)
Monetary policy (Federal Reserve actions, interest rates)
Policy that directly involves with the economy
Trade policy (Examples: tariffs, trade agreements, import/export regulations)
Economic forecasts or recession/expansion predictions
Currency markets and exchange rates
National or global economic conditions and trends

If the article discusses, in text, theme, or content, policy debates or legislation without electoral context, then it can be marked as 'other', among any other applicable categories
Multiple mentions of the same sectoral crisis (e.g., 'The Farm Vote,' 'Farm Revolt,' 'Farm Distress') count as one single thematic mention. To reach a classification of ECONOMY, the article must discuss at least three different economic topics.


—-End Categories Criteria—---


Return ONLY a CSV with exactly THREE columns and NO additional text:

Column 1: new_filename (the article identifier)
Column 2: category (one or more classifications separated by semicolons)
Column 3: explanation (brief justification citing specific counts)

- Include a header row: new_filename,category,explanation
- No quotes around values unless they contain commas
- Multiple categories in alphabetical order separated by semicolons
- Explanation must specify the count for each assigned category
- Maximum 15 words per explanation

Examples:
article2.txt,economy,`4 company strategy mentions, 2 GDP references'
article3.txt,other, `No categories met the 2-mention threshold.” 

No other explanation is required for 'other'.

IMPORTANT: YOU MUST PROCESS EACH ENTRY IN THE SOURCE DATA. PREVIOUS CLASSIFICATIONS HAVE STOPPED ABOUT 3/4s through. EXAMINE EACH ENTRY IN THE DATA."
)

```

### Business

```{r}
chat_biz <- chat_google_gemini(system_prompt =  "You are an academic researcher performing context analysis on selected news articles. Analyze each article and classify it based on specified criteria.

In this prompt, the phrases “category” and “classification” and any of their grammatical variations are synonymous. 

An article should receive a classification if it meets the requirements for the category specified below. Each article must independently meet a threshold of three or more mentions of specified criteria to be included in a specific category.

If an article meets none of the criteria, classify it as 'other'


—-Start Categories Criteria—---

BUSINESS: an article contains three or more, in text, content, or theme, mentions of 
Companies, Corporate entities, their operations, or strategic decisions
Executives, Business leaders, appointments, departures, or leadership actions
Product launches and announcements
Marketing campaigns
Regulatory compliance matters
Mergers and acquisitions
Partnerships and collaborations between companies or other industry groups
Corporate strategy changes
Financial Dealings common to business (examples: Earnings, investments, funding, stock performance, financial results)
Industry, Sector trends, market analysis, competitive dynamics
Terms as 'private enterprise', 'company', 'firm', 'business leaders', 'businessmen',

For the above categories, there are some topics that could create a classification “gray area”. For the purposes of this research, use the following descriptions to validate classifications.  Any article that any of these apply to can still be categorized as multiple categories.

If the article discusses, in text, theme, or content, individual company financial performance, classify it as 'business', among any other applicable categories
If the article discusses, in text, theme, or content, industry-specific trends without macroeconomic context → classify as 'business'
If the article discusses, in text, theme, or content, stock market movements alone without broader economic analysis or context, classify it as 'business', among any other applicable categories
If the article discusses, in text, theme, or content, labor issues such as strikes, unionization, worker disputes, classify it as ‘other’, not ‘business’, among any other applicable categories
If the article only mentions a company tangentially (e.g., 'Apple CEO attended a charity gala') without discussing business matters, it does not fall under ‘business’

—-End Categories Criteria—---


Return ONLY a CSV with exactly THREE columns and NO additional text:

Column 1: new_filename (the article identifier)
Column 2: category (one or more classifications separated by semicolons)
Column 3: explanation (brief justification citing specific counts)

- Include a header row: new_filename,category,explanation
- No quotes around values unless they contain commas
- Multiple categories in alphabetical order separated by semicolons
- Explanation must specify the count for each assigned category
- Maximum 15 words per explanation

Examples:
article2.txt,business,`4 company strategy mentions, 2 GDP references'
article3.txt,other, `No categories met the 2-mention threshold.” 

No other explanation is required for 'other'.

IMPORTANT: YOU MUST PROCESS EACH ENTRY IN THE SOURCE DATA. PREVIOUS CLASSIFICATIONS HAVE STOPPED ABOUT 3/4s through. EXAMINE EACH ENTRY IN THE DATA."
)

```
### Labor

```{r}
chat_labor <- chat_google_gemini(system_prompt =  "You are an academic researcher performing context analysis on selected news articles. Analyze each article and classify it based on specified criteria.

In this prompt, the phrases “category” and “classification” and any of their grammatical variations are synonymous. 

An article should receive a classification if it meets the requirements for the category specified below. Each article must independently meet a threshold of three or more mentions of specified criteria to be included in a specific category.

If an article meets none of the criteria, classify it as 'other'


—-Start Categories Criteria—---


LABOR: an article contains three or more, in text, content, or theme,

Strikes or work stoppages
Unionization efforts
Union elections
Worker disputes involving unions or collective bargaining
Public policy issues focusing on organized labor (Examples: llabor law reforms, right-to-work legislation)
Statements or actions by union leaders or labor organizations
Terms such as 'AFL' and or 'CIO' (Congress of Industrial Organizations)

For the above categories, there are some topics that could create a classification “gray area”. For the purposes of this research, use the following descriptions to validate classifications.  Any article that any of these apply to can still be categorized as multiple categories.

—-End Categories Criteria—---


Return ONLY a CSV with exactly THREE columns and NO additional text:

Column 1: new_filename (the article identifier)
Column 2: category (one or more classifications separated by semicolons)
Column 3: explanation (brief justification citing specific counts)

- Include a header row: new_filename,category,explanation
- No quotes around values unless they contain commas
- Multiple categories in alphabetical order separated by semicolons
- Explanation must specify the count for each assigned category
- Maximum 15 words per explanation

Examples:
article2.txt,business;economy,`4 company strategy mentions, 2 GDP references'
article3.txt,other, `No categories met the 2-mention threshold.” 

No other explanation is required for 'other'.

IMPORTANT: YOU MUST PROCESS EACH ENTRY IN THE SOURCE DATA. PREVIOUS CLASSIFICATIONS HAVE STOPPED ABOUT 3/4s through. EXAMINE EACH ENTRY IN THE DATA."
)

```

# LLM call & API pause
```{r}
# --- 2. RESET STORAGE ---
# Clear out previous runs to avoid mixing old duplicated data with this clean data
if(dir.exists("batch_results")) unlink("batch_results", recursive = TRUE)
dir.create("batch_results")

# --- 3. THE RESUMABLE BATCH FUNCTION ---
run_biz_batch <- function(batch_data) {
  current_b <- unique(batch_data$batch_id)
  total_b <- max(processed_llm$batch_id)
  batch_file <- paste0("batch_results/batch_", current_b, ".txt")
  
  # IF FILE EXISTS: Load it and skip the API call
  if(file.exists(batch_file)) {
    message(paste0("Skipping Batch ", current_b, ": Already processed."))
    return(readr::read_file(batch_file))
  }
  
  # ELSE: Format and send to Gemini
  batch_text <- batch_data %>%
    mutate(formatted = paste0("FILENAME: ", new_filename, "\nCONTENT: ", full_text)) %>%
    pull(formatted) %>%
    paste(collapse = "\n\n---ARTICLE SEPARATOR---\n\n")
  
  message(paste0("--- Processing Batch ", current_b, " of ", total_b, " ---"))
  
#-----------------------------------------------------------------------------  
# The API Call
  #change variable according to text
#  response <- chat_biz$chat(batch_text)
response <- chat_labor$chat(batch_text)  
#    response <- chat_econ$chat(batch_text)  
  
#  response <- chat_voter$chat(batch_text)
#    response <- chat_politics$chat(batch_text)  
  
  
#-----------------------------------------------------------------------------  
  # SAVE immediately to your hard drive
  readr::write_file(response, batch_file)
  
  # Delay to respect rate limits
  if (current_b < total_b) {
    message("Waiting 5 seconds for rate limits...")
    Sys.sleep(5)
  }
  
  return(response)
}

# --- 4. RUN THE LOOP ---
# Even if this crashes, the files in 'batch_results' stay safe!
raw_batch_results <- processed_llm %>%
  group_split(batch_id) %>%
  map_chr(run_biz_batch)

# --- 5. COMBINE RESULTS ---
final_output_text <- paste(raw_batch_results, collapse = "\n")

# Save a master backup of the whole thing
write_lines(final_output_text, "final_classifications.csv")

message("All articles processed successfully!")
```

```{r}

# 1. Strip all Markdown backticks and the "csv" label
# We use str_trim to remove leading/trailing whitespace/newlines
clean_text <- final_output_text %>%
  str_remove_all("```csv") %>%
  str_remove_all("```") %>%
  str_trim()

# 2. Parse into a Data Frame
results_df <- read_csv(
    I(clean_text), 
    col_names = c("new_filename", "category", "explanation"), # Manually set names
    show_col_types = FALSE
  ) %>%
  # 3. Clean up the rows
  filter(
    !is.na(new_filename),               # Remove empty rows
    new_filename != "new_filename",     # Remove any AI-generated headers
    str_detect(new_filename, "\\.txt")  # Ensure row looks like a filename
  ) %>%
  # 4. Remove any duplicates
  distinct(new_filename, .keep_all = TRUE)

# View a summary
print(paste("Successfully parsed", nrow(results_df), "articles."))
```

### Rename df 
change variable according to data being processed - voter, biz etc

```{r}

#politics_results_df <- results_df
```

#Combine dfs
```{r}
biz <- biz_results_df |> 
  rename(biz_category = category, biz_explanation = explanation)
voter <- voter_results_df |> 
  rename(voter_category = category, voter_explanation = explanation)
politics <- politics_results_df |> 
  rename(politics_category = category, politics_explanation = explanation)

validate_new <- list(biz, voter, politics) |> 
  reduce(full_join, by = "new_filename")

validate_new <- validate_new |> 
  mutate(all_categories = paste0(biz_category, "; ", voter_category, "; ",politics_category)) |> 
  mutate(all_categories = str_remove_all(all_categories, "\\bother\\b;?\\s*|;?\\s*\\bother\\b"))

```

### Counts

```{r}
counts <- validate_new %>%
  # 1. Split the category column by the semicolon
  separate_rows(all_categories, sep = ";") %>%
  # 2. Clean up any accidental leading/trailing spaces the AI might have left
  mutate(all_categories = str_trim(all_categories)) |> 
  count(all_categories, sort = TRUE)


	
# all_categories n 
# politics 83
# voter_turnout 50
# economy 45
# business 35
# labor 34
```




### Combine categories with main data
```{r}


validate_new <- validate_new |> 
  inner_join(tighter, by=c("new_filename"))

validate_new <- validate_new |> 
  select(new_filename, date, year, title, full_text, everything())


write_csv(validate_new, "./output/validate_new_jan9.csv")

validate_brief <- validate_new |> 
  select(filename, date, year, title, full_text, biz_category, biz_explanation, voter_category, voter_explanation, politics_category, politics_explanation) |> 
  mutate(correct_y_n = "")

write_csv(validate_brief, "./output/validate_brief_new_jan7.csv")

```

# Validation

### Print out articles for verification
```{r}

# Now create the text file with locations highlighted
file_conn <- file("ai_classifier_moley_verify.txt", "w")

for (i in 1:nrow(validate_new)) {
  row_data <- validate_new[i, ]
  
  writeLines(paste0("Document ID: ", row_data$new_filename), file_conn)
  writeLines(paste0("Date: ", row_data$date), file_conn)
  writeLines(paste0("Headline: ", row_data$title), file_conn)
  writeLines(paste0("-------------"), file_conn)
  writeLines(paste0("Biz Category: ", row_data$biz_category), file_conn)
  writeLines(paste0("AI Biz Explanation: ", row_data$biz_explanation), file_conn)
   writeLines(paste0("-------------"), file_conn)
  writeLines(paste0("Voter Category: ", row_data$voter_category), file_conn)
  writeLines(paste0("AI Voter Explanation: ", row_data$voter_explanation), file_conn)
   writeLines(paste0("-------------"), file_conn)
  writeLines(paste0("Politics Category: ", row_data$politics_category), file_conn)
  writeLines(paste0("AI Politics Explanation: ", row_data$politics_explanation), file_conn)
   writeLines(paste0("-------------"), file_conn)
  # Wrap the full text
  wrapped_text <- strwrap(row_data$full_text, width = 80)
  wrapped_text[1] <- paste0("Article Text: ", wrapped_text[1])
  writeLines(wrapped_text, file_conn)
  
  if (i < nrow(validate)) {
    writeLines("\n==================================================\n", file_conn)
  }
}

close(file_conn)
```

### Quick view of any entry by row
```{r}
wrapped_text <- strwrap(as.character(combo$jan7_explanation[92]), width = 60)
writeLines(wrapped_text, "temp_text.txt")
file.edit("temp_text.txt")
```


#The Timeline Visualization Script

```{r}
# 1. Prepare the data for plotting
plot_data <- validate_new %>%
  # Split the categories into individual rows
  separate_rows(all_categories, sep = ";") %>%
  mutate(all_categories = str_trim(all_categories)) %>%
  # Filter to focus on the core themes (optional: remove 'other')
  filter(all_categories %in% c("business", "labor", "economy")) %>%
  # Ensure the date column is a Date object and floor it to the start of the month
  mutate(
    date = as.Date(date),
    month = floor_date(date, "month")
  ) %>%
  # Count occurrences of each all_categories per month
  count(month, all_categories)

# 2. Create the Timeline Plot
ggplot(plot_data, aes(x = month, y = n, color = all_categories, group = all_categories)) +
  # Add points and lines
  geom_line(size = 1.2, alpha = 0.7) +
  geom_point(size = 3) +
  # Formatting the scales
  scale_x_date(date_breaks = "1 month", date_labels = "%b") +
  scale_color_manual(values = c(
    "business" = "#2C3E50", # Dark Blue
    "labor" = "#E74C3C",    # Red
    "economy" = "#27AE60"   # Green
  )) +
  # Labels and Theme
  labs(
    title = "Coverage Trends in 1956",
    subtitle = "Monthly frequency of mentions by category",
    x = "Month of 1956",
    y = "Number of Articles",
    color = "Category"
  ) +
  theme_minimal() +
  theme(
    legend.position = "bottom",
    plot.title = element_text(face = "bold", size = 16),
    panel.grid.minor = element_blank()
  )
```

#------OLDER-----------------
count the results
```{r}
lat_1956_politics |> 
  count(category) |> 
  arrange(desc(n))

#politics:
# 1    other 20
# 2 politics 88
# voter_turnout	54			
# other	52	
# other	33			
# labor classification	26			
# economy	19			
# economy;labor classification	9			
# business	8			
# business;labor classification	7			
# business;economy	4			
# business;economy;labor classification	2	

#tighter = 3 or more
# politics	81			
# other	27	
# other	58			
# voter_turnout	50	
# other	28			
# economy	10			
# business	7			
# business;economy	7			
# labor	5			
# economy;labor	2			
# 1			
# business;economy;labor	1			
# business;labor	1	

```

#Compare the results
```{r}
july24 <- rio::import("https://docs.google.com/spreadsheets/d/1Y-IWU_AgbyE-2G2jyT15MIO2jtv_Qpgi1imRwKTjPHQ/edit?gid=1373544130#gid=1373544130", which = "July24_results", header = TRUE) |> 
  clean_names()

oct20 <- rio::import("https://docs.google.com/spreadsheets/d/1Y-IWU_AgbyE-2G2jyT15MIO2jtv_Qpgi1imRwKTjPHQ/edit?gid=1553901874#gid=1553901874", which = "Oct20_results", header = TRUE) |> 
  clean_names() 


```


### Process to join
Politics
```{r}
july24_clean <- july24 |> 
  select(filename, category, explanation, correct, human_comments) |> 
  rename(july24_category = category, july24_explanation = explanation, july24_correct = correct, july24_human_comments = human_comments)
oct20_clean <- oct20 |> 
  select(filename, category, explanation) |> 
  rename(oct20_category = category, oct_20explanation = explanation)


#change variable names for voter, politics etc
jan_7 <- lat_1956_biz |> 
   rename(jan7_category = category, jan7_explanation = explanation)

combo <- oct20_clean |> 
  right_join(july24_clean, by ="filename") |> 
  right_join(jan_7, by = "filename")


#split crime1 into three new columns
combo <- separate(data = combo, col = jan7_category, into = c("jan7_category1", "jan7_category2"), sep = ";", extra = "merge", fill = "right")
combo <- separate(data = combo, col = oct20_category, into = c("Oct20_category1", "Oct20_category2"), sep = ";", extra = "merge", fill = "right")
combo <- separate(data = combo, col = july24_category, into = c("july24_category1", "july24_category2"), sep = ";", extra = "merge", fill = "right")




# combo <- jan_7 |> 
#   right_join(combo, by ="filename")


```






### Analyze differences
```{r}
diffs_biz <- combo |> 
  mutate(changed_july24 = case_when(
    jan7_category1 == july24_category1 ~ "same",
    jan7_category1 != july24_category1 ~ "different",
    jan7_category2 == july24_category2 ~ "same",
    jan7_category2 != july24_category2 ~ "different",
    .default = NA_character_
  )) |> 
    mutate(changed_oct20 = case_when(
    jan7_category1 == Oct20_category1 ~ "same",
    jan7_category1 != Oct20_category1 ~ "different",
    jan7_category2 == Oct20_category2 ~ "same",
    jan7_category2 != Oct20_category2 ~ "different",
    .default = NA_character_
  )) |> 
  
  select(changed_july24, jan7_category1, jan7_category2, july24_category1, jan7_category1, jan7_category2, july24_category2, changed_oct20, jan7_category1, jan7_category2, Oct20_category1, Oct20_category2, july24_correct, july24_human_comments, everything())

write_csv(diffs_biz, "./output/jan7_biz_july24_diffs.csv")
```

```{r}
diffs_voter <- read_csv("./output/jan7_voter_july24_diffs.csv")
diffs_biz <- read_csv("./output/jan7_biz_july24_diffs.csv")

```


### Count categories
```{r}

current_counts <- combo |>
  select(filename, jan7_category1, jan7_category2) |>
  pivot_longer(cols = c(jan7_category1, jan7_category2), 
               names_to = "category_type", 
               values_to = "category") |>
  filter(!is.na(category)) |>
  count(category, name = "current_count")

# Count all july24_category1 and july24_category2 together
oct20_counts <- combo |>
  select(filename, Oct20_category1, Oct20_category2) |>
  pivot_longer(cols = c(Oct20_category1, Oct20_category2), 
               names_to = "category_type", 
               values_to = "category") |>
  filter(!is.na(category)) |>
  count(category, name = "Oct20_count")

# Count all july24_category1 and july24_category2 together
july24_counts <- combo |>
  select(filename, july24_category1, july24_category2) |>
  pivot_longer(cols = c(july24_category1, july24_category2), 
               names_to = "category_type", 
               values_to = "category") |>
  filter(!is.na(category)) |>
  count(category, name = "july24_count")



# comparison_voter <- comparison



comparison_biz <- list(current_counts, oct20_counts, july24_counts) |> 
  reduce(full_join, by = "category") |> 
  arrange(desc(current_count))

# # Combine them side by side
# comparison_biz <- current_counts |> 
#   full_join(oct20_counts, by = "category") |> 
#   full_join(july24_counts, by = "category") |> # Now it's properly included
#   replace_na(list(current_count = 0, Oct20_count = 0, july24_count = 0)) |> 
#   arrange(desc(current_count))
```


#---------Notes on rate limit ---------------
Aug 20
unclear if it is using my robwells21032@gmail or robwells@umd.edu


Waiting 5 seconds for rate limits...
--- Processing Batch 67 of 120 ---
Error in `map_chr()`:
ℹ In index: 67.
Caused by error in `req_perform_connection()`:
! HTTP 429 Too Many Requests.
ℹ You exceeded your current quota, please check your plan and billing details. For more
  information on this error, head to: https://ai.google.dev/gemini-api/docs/rate-limits. To
  monitor your current usage, head to: https://ai.dev/rate-limit.  * Quota exceeded for metric:
  generativelanguage.googleapis.com/generate_content_paid_tier_2_input_token_count, limit:
  3000000, model: gemini-3.5-flash Please retry in 41.713333453s.
Run `rlang::last_trace()` to see where the error occurred.



There is a crucial distinction behind why this happened: A paid consumer subscription (like Gemini Advanced / Google AI Pro) is completely separate from API billing.Your $20/month subscription only applies to the consumer web chat at gemini.google.com. Generating an API key in Google AI Studio or Google Cloud starts you on the Free Tier for the API, which carries very strict rate limits regardless of your personal Google account's subscription status.  1. Enable Pay-As-You-Go Billing for the APITo remove the restrictive Free Tier limits, you must explicitly link a billing account to your developer project in Google AI Studio:Go to Google AI Studio and open the Billing / Projects tab.  Click Set up billing on the project associated with your API key.  Add a payment method and prepay/link billing.  Upgrading to Tier 1 (Pay-As-You-Go) expands your throughput dramatically:  Free Tier: ~5–15 Requests Per Minute (RPM), capped at ~100 Requests Per Day (RPD) depending on the model.  Tier 1 Paid: 150–300 Requests Per Minute (RPM) and up to 1,500 Requests Per Day.  2. Multi-Dimensional Rate Limits (Why your pause failed)Even on a paid API tier, rate limits are checked across four separate metrics simultaneously:  RPM (Requests Per Minute)  TPM (Tokens Per Minute — input context + generated output)  RPD (Requests Per Day)  Rolling 10-Minute Spend Caps  If you send massive prompts or large datasets (like long text files or audio/video inputs), you likely hit the TPM (Tokens Per Minute) limit rather than the request count limit. A simple pause between requests prevents high RPM, but if each prompt is large, your total tokens per minute will still trigger a 429 RESOURCE_EXHAUSTED error.  3. Updating Your Script for ReliabilityRather than relying solely on fixed sleeps/pauses, wrap your script in Exponential Backoff logic. This automatically intercepts rate-limit errors and pauses dynamically until your token bucket resets.Python Example using tenacity or time.sleep:Pythonimport time
from google.api_core.exceptions import ResourceExhausted

xxx

def call_gemini_with_retry(prompt, retries=5):
    for attempt in range(retries):
        try:
            response = model.generate_content(prompt)
            return response.text
        except ResourceExhausted:
            wait_time = (2 ** attempt) * 5  # Exponential wait: 5s, 10s, 20s, 40s...
            print(f"Rate limit hit. Waiting {wait_time}s before retrying...")
            time.sleep(wait_time)
    raise Exception("Max retries exceeded")
R Example using tryCatch:Rcall_gemini <- function(prompt, retries = 5) {
  for (i in 1:retries) {
    result <- tryCatch({
      # Your Gemini API call code here
      return(response)
    }, error = function(e) {
      if (grepl("429|RESOURCE_EXHAUSTED", e$message)) {
        wait_time <- (2 ^ i) * 5
        message(sprintf("Rate limit hit. Waiting %d seconds...", wait_time))
        Sys.sleep(wait_time)
        return(NULL)
      } else {
        stop(e)
      }
    })
    if (!is.null(result)) return(result)
  }
  stop("Max retries exceeded.")
}

