---
title: "AI Classifier"
output: null
date: 1-7-2026
---

```{r}
#install.packages("ellmer")
library(ellmer)
library(tidyverse)
library(glue)
library(janitor)
library(purrr)

#Sys.setenv(GOOGLE_API_KEY = "")

```

#Check Gemini is working

```{r}
chat <- chat_google_gemini()

chat$chat("Tell me four jokes about data journalists")
```
# LAT Data
## Load LAT Data
```{r echo = F}
#2501 articles in index
lat_article_index <-  rio::import("/Users/gizmofo/Library/CloudStorage/Dropbox/Current_Projects/Moley project 2024/Indexes of Moley Articles/lat_txt_index_renamed_7_23.csv") |> 
  clean_names() |> 
  mutate(year = lubridate::year(date))
  

#284067 rows of text
lat_articles_text <-  read_csv("/Users/gizmofo/Library/CloudStorage/Dropbox/Current_Projects/Moley project 2024/Indexes of Moley Articles/moley_lat_text_june_21.csv") |>
   clean_names() |>
    mutate(year = as.numeric(year)) |> 
  mutate(new_filename = paste0(date,"_",filename))

# lat_articles_text <- experiment
```
###Collapse article text into single column
```{r}

llm_lat <- lat_articles_text |> 
  group_by(filename) |> 
  summarize(
    # Join only non-NA sentences, then fix those line-break hyphens
    full_text = paste(na.omit(sentence), collapse = " ") |> 
                str_replace_all("- ", ""),
    
    # Keep metadata by looking for the first NON-NA value in each column
    across(everything(), \(x) first(na.omit(x)))
  ) |> 
  ungroup() |> 
  filter(year =="1956")

```


```{r}
process_articles <- function(df) {
  # First group by article identifiers and concatenate sentences
  # Using filename as the identifier, but you might need to use other columns
  compiled_df <- df %>%
    group_by(new_filename) %>%
    summarize(
      sentence = paste(na.omit(sentence), collapse = " "),
      title = first(title),
      abstract = first(abstract),
      authors = first(authors),
      filepath = first(filepath),
      index = first(index),
      issn = first(issn),
      pages = first(pages),
      title = first(title),
      year = first(year),
      document_url = first(document_url),
      find_a_copy = first(find_a_copy),
      date = first(date),
      year=first(year)
    )
  
  # Remove punctuation and spaces from the sentence column
  compiled_df <- compiled_df %>%
    mutate(sentence = str_replace_all(sentence, "[[:punct:][:space:]]", "")) |> 
    mutate(sentence = tolower(sentence))
  
  return(compiled_df)
}

# Make sure to load the necessary libraries
library(dplyr)
library(stringr)

# Apply the function to your dataframe
processed_llm_test <- process_articles(llm_lat)
```

```{r}
# Prepare data with filenames and content
articles_for_analysis <- processed_llm_test %>%
  select(new_filename, sentence) %>%
  mutate(article_data = paste("FILENAME:", new_filename, "\nCONTENT:", sentence))

# Combine with clear separators
combined_text_with_filenames <- paste(articles_for_analysis$article_data, 
                                    collapse = "\n\n---ARTICLE SEPARATOR---\n\n")
```

# LLM Prompt


### Politics
Using model = "gemini-2.5-flash".

```{r}
chat_politics <- chat_google_gemini(system_prompt = "You are an academic researcher performing context analysis on selected news articles. Analyze each article and classify it based on specified criteria.

In this prompt, the phrases “category” and “classification” and any of their grammatical variations are synonymous. 

An article should receive a classification if it meets the requirements for the category specified below. Each article must independently meet a threshold of three or more mentions of specified criteria to be included in a specific category.

If an article meets none of the criteria, classify it as 'other'

—-Start Category Criteria—---

POLITICS: an article contains, in text, content, or theme, three or more of the following

- Voting in a political election
- Upcoming elections (primaries, general elections, special elections)
- Election results and outcomes
- Political campaigns
- Political campaign strategies
- Candidate announcements, debates, or endorsements
- Election polling and predictions
- Political party activities related to elections
- Specific words: “election”, “vote”, “polls”, “ballots”, “candidate”


For the above category, there are some topics that could create a classification “gray area”. For the purposes of this research, use the following descriptions to validate classifications.  Any article that any of these apply to can still be categorized as multiple categories.

If the article discusses, in text, theme, or content, policy debates or legislation without electoral context, then it can be marked as 'other', among any other applicable categories
If the article discusses, in text, theme, or content, appointed officials or bureaucratic actions, then it is not ‘politics’ category unless the discussion is tied to an election

—-End Category Criteria—---


Return ONLY a CSV with exactly THREE columns and NO additional text:

Column 1: new_filename (the article identifier)
Column 2: category 
Column 3: explanation (brief justification citing specific counts)

- Include a header row: new_filename,category,explanation
- No quotes around values unless they contain commas
- Multiple categories in alphabetical order separated by semicolons
- Explanation must specify the count for each assigned category
- Maximum 15 words per explanation

Examples:
article1.txt,politics,`3 mentions of election campaigns, 2 candidate endorsements`
No other explanation is required for 'other'."
)

```

### Voter_Turnout

```{r}
chat_voter <- chat_google_gemini(system_prompt =  "You are an academic researcher performing context analysis on selected news articles. Analyze each article and classify it based on specified criteria.

In this prompt, the phrases “category” and “classification” and any of their grammatical variations are synonymous. 

An article should receive a classification if it meets the requirements for the category specified below. Each article must independently meet a threshold of three or more mentions of specified criteria to be included in a specific category.

If an article meets none of the criteria, classify it as 'other'


—-Start Categories Criteria—---

VOTER TURNOUT: an article contains three or more,  in text, content, or theme, mentions of 
Amount of people participating in voting during an election
Voter registration drives or registration statistics
Early voting, absentee voting, or mail-in ballot usage
Voter turnout rates or participation levels
Efforts to get people to vote in elections
Barriers to voting or voter access issues (polling locations, ID requirements, wait times)
Specific details about voter participation in an election
Efforts supress or discourage people from voting in elections



—-End Categories Criteria—---


Return ONLY a CSV with exactly THREE columns and NO additional text:

Column 1: new_filename (the article identifier)
Column 2: category (one or more classifications separated by semicolons)
Column 3: explanation (brief justification citing specific counts)

- Include a header row: new_filename,category,explanation
- No quotes around values unless they contain commas
- Multiple categories in alphabetical order separated by semicolons
- Explanation must specify the count for each assigned category
- Maximum 15 words per explanation

Examples:
article1.txt,voter_turnout,`3 mentions of Voter registration drives, 2 Get-out-the-vote efforts` 

No other explanation is required for 'other'."
)

```

### Business

```{r}
chat_biz <- chat_google_gemini(system_prompt =  "You are an academic researcher performing context analysis on selected news articles. Analyze each article and classify it based on specified criteria.

In this prompt, the phrases “category” and “classification” and any of their grammatical variations are synonymous. 

An article should receive a classification if it meets the requirements for the category specified below. Each article must independently meet a threshold of three or more mentions of specified criteria to be included in a specific category.

If an article meets none of the criteria, classify it as 'other'


—-Start Categories Criteria—---

ECONOMY:  an article contains three or more,  in text, content, or theme, mentions of 
Macroeconomic issues or economic policy.
Macroeconomic indicators (Examples: GDP, inflation, unemployment rates, economic growth)
Monetary policy (Federal Reserve actions, interest rates)
Policy that directly involves with the economy
Trade policy (Examples: tariffs, trade agreements, import/export regulations)
Economic forecasts or recession/expansion predictions
Currency markets and exchange rates
National or global economic conditions and trends

BUSINESS: an article contains three or more, in text, content, or theme, mentions of 
Companies, Corporate entities, their operations, or strategic decisions
Executives, Business leaders, appointments, departures, or leadership actions
Product launches and announcements
Marketing campaigns
Regulatory compliance matters
Mergers and acquisitions
Partnerships and collaborations between companies or other industry groups
Corporate strategy changes
Financial Dealings common to business (examples: Earnings, investments, funding, stock performance, financial results)
Industry, Sector trends, market analysis, competitive dynamics
Terms as 'private enterprise', 'company', 'firm', 'business leaders', 'businessmen',

LABOR CLASSIFICATION: an article contains three or more, in text, content, or theme,

Strikes or work stoppages
Unionization efforts
Union elections
Worker disputes involving unions or collective bargaining
Public policy issues focusing on organized labor (Examples: llabor law reforms, right-to-work legislation)
Statements or actions by union leaders or labor organizations
Terms such as 'AFL' and or 'CIO' (Congress of Industrial Organizations)

For the above categories, there are some topics that could create a classification “gray area”. For the purposes of this research, use the following descriptions to validate classifications.  Any article that any of these apply to can still be categorized as multiple categories.

If the article discusses, in text, theme, or content, policy debates or legislation without electoral context, then it can be marked as 'other', among any other applicable categories
If the article discusses, in text, theme, or content, individual company financial performance, classify it as 'business', among any other applicable categories
If the article discusses, in text, theme, or content, industry-specific trends without macroeconomic context → classify as 'business'
If the article discusses, in text, theme, or content, stock market movements alone without broader economic analysis or context, classify it as 'business', among any other applicable categories
If the article discusses, in text, theme, or content, labor issues such as strikes, unionization, worker disputes, classify it as ‘labor’, not ‘business’, among any other applicable categories
If the article only mentions a company tangentially (e.g., 'Apple CEO attended a charity gala') without discussing business matters, it does not fall under ‘business’


—-End Categories Criteria—---


Return ONLY a CSV with exactly THREE columns and NO additional text:

Column 1: new_filename (the article identifier)
Column 2: category (one or more classifications separated by semicolons)
Column 3: explanation (brief justification citing specific counts)

- Include a header row: new_filename,category,explanation
- No quotes around values unless they contain commas
- Multiple categories in alphabetical order separated by semicolons
- Explanation must specify the count for each assigned category
- Maximum 15 words per explanation

Examples:
article2.txt,business;economy,`4 company strategy mentions, 2 GDP references'
article3.txt,other, `No categories met the 2-mention threshold.” 

No other explanation is required for 'other'.

IMPORTANT: YOU MUST PROCESS EACH ENTRY IN THE SOURCE DATA. PREVIOUS CLASSIFICATIONS HAVE STOPPED ABOUT 3/4s through. EXAMINE EACH ENTRY IN THE DATA."
)

```


<!-- # Biz chat to the LLM -->
<!-- ```{r} -->
<!-- biz<- chat_biz$chat(combined_text_with_filenames) -->
<!-- ``` -->

<!-- # Voter chat to the LLM -->
<!-- ```{r} -->
<!-- voter<- chat_voter$chat(combined_text_with_filenames) -->
<!-- ``` -->

# New LLM call with api pause
```{r}
# --- 1. PREPARE THE DATA ---
process_articles <- function(df) {
  df %>%
    group_by(new_filename) %>%
    summarize(
      full_text = paste(na.omit(full_text), collapse = " ") %>% 
                  str_replace_all("- ", "") %>% 
                  str_squish(),
      across(c(date, year, title, abstract, authors, document_url), \(x) first(na.omit(x)))
    ) %>%
    ungroup()
}

processed_llm_test <- process_articles(llm_lat) |> 
  distinct(new_filename, .keep_all = TRUE)

# Add Batch IDs (10 articles per batch)
# Assign fresh Batch IDs
processed_llm_test <-processed_llm_test|>
  mutate(batch_id = ceiling(row_number() / 10))


unlink("batch_results", recursive = TRUE)
dir.create("batch_results")

# --- 2. SETUP RESUMABLE STORAGE ---
# Creates a folder called 'batch_results' in your working directory
if(!dir.exists("batch_results")) dir.create("batch_results")


# --- 3. THE RESUMABLE BATCH FUNCTION ---
run_biz_batch <- function(batch_data) {
  current_b <- unique(batch_data$batch_id)
  total_b <- max(processed_llm_test$batch_id)
  batch_file <- paste0("batch_results/batch_", current_b, ".txt")
  
  # IF FILE EXISTS: Load it and skip the API call
  if(file.exists(batch_file)) {
    message(paste0("Skipping Batch ", current_b, ": Already processed."))
    return(readr::read_file(batch_file))
  }
  
  # ELSE: Format and send to Gemini
  batch_text <- batch_data %>%
    mutate(formatted = paste0("FILENAME: ", new_filename, "\nCONTENT: ", full_text)) %>%
    pull(formatted) %>%
    paste(collapse = "\n\n---ARTICLE SEPARATOR---\n\n")
  
  message(paste0("--- Processing Batch ", current_b, " of ", total_b, " ---"))
  
#-----------------------------------------------------------------------------  
# The API Call
  #change variable according to text
#  response <- chat_biz$chat(batch_text)
#  response <- chat_voter$chat(batch_text)
    response <- chat_politics$chat(batch_text)  
  
  
#-----------------------------------------------------------------------------  
  # SAVE immediately to your hard drive
  readr::write_file(response, batch_file)
  
  # Delay to respect rate limits
  if (current_b < total_b) {
    message("Waiting 5 seconds for rate limits...")
    Sys.sleep(5)
  }
  
  return(response)
}

# --- 4. RUN THE LOOP ---
# Even if this crashes, the files in 'batch_results' stay safe!
raw_batch_results <- processed_llm_test %>%
  group_split(batch_id) %>%
  map_chr(run_biz_batch)

# --- 5. COMBINE RESULTS ---
final_output_text <- paste(raw_batch_results, collapse = "\n")

# Save a master backup of the whole thing
write_lines(final_output_text, "final_classifications.csv")

message("All articles processed successfully!")
```

```{r}

# 1. Strip all Markdown backticks and the "csv" label
# We use str_trim to remove leading/trailing whitespace/newlines
clean_text <- final_output_text %>%
  str_remove_all("```csv") %>%
  str_remove_all("```") %>%
  str_trim()

# 2. Parse into a Data Frame
results_df <- read_csv(
    I(clean_text), 
    col_names = c("new_filename", "category", "explanation"), # Manually set names
    show_col_types = FALSE
  ) %>%
  # 3. Clean up the rows
  filter(
    !is.na(new_filename),               # Remove empty rows
    new_filename != "new_filename",     # Remove any AI-generated headers
    str_detect(new_filename, "\\.txt")  # Ensure row looks like a filename
  ) %>%
  # 4. Remove any duplicates
  distinct(new_filename, .keep_all = TRUE)

# View a summary
print(paste("Successfully parsed", nrow(results_df), "articles."))

#change variable according to data being processed
politics_results_df <- results_df
```

#Combine dfs
```{r}
biz <- biz_results_df |> 
  rename(biz_category = category, biz_explanation = explanation)
voter <- voter_results_df |> 
  rename(voter_category = category, voter_explanation = explanation)
politics <- politics_results_df |> 
  rename(politics_category = category, politics_explanation = explanation)

validate_new <- list(biz, voter, politics) |> 
  reduce(full_join, by = "new_filename")

validate_new <- validate_new |> 
  mutate(all_categories = paste0(biz_category, "; ", voter_category, "; ",politics_category)) |> 
  mutate(all_categories = str_remove_all(all_categories, "\\bother\\b;?\\s*|;?\\s*\\bother\\b"))

```

### Counts

```{r}
counts <- validate_new %>%
  # 1. Split the category column by the semicolon
  separate_rows(all_categories, sep = ";") %>%
  # 2. Clean up any accidental leading/trailing spaces the AI might have left
  mutate(all_categories = str_trim(all_categories)) |> 
  count(all_categories, sort = TRUE)


	
# all_categories n 
# politics 83
# voter_turnout 50
# economy 45
# business 35
# labor 34
```

### Combine categories with main data
```{r}


validate_new <- validate_new |> 
  inner_join(tighter, by=c("new_filename"))

validate_new <- validate_new |> 
  select(new_filename, date, year, title, full_text, everything())


write_csv(validate_new, "./output/validate_wew_jan8.csv")

validate_brief <- validate_new |> 
  select(filename, date, year, title, full_text, biz_category, biz_explanation, voter_category, voter_explanation, politics_category, politics_explanation) |> 
  mutate(correct_y_n = "")

write_csv(validate_brief, "./output/validate_brief_new_jan7.csv")

```

#Print out articles for verification
```{r}

# Now create the text file with locations highlighted
file_conn <- file("ai_classifier_moley_verify.txt", "w")

for (i in 1:nrow(validate_new)) {
  row_data <- validate_new[i, ]
  
  writeLines(paste0("Document ID: ", row_data$new_filename), file_conn)
  writeLines(paste0("Date: ", row_data$date), file_conn)
  writeLines(paste0("Headline: ", row_data$title), file_conn)
  writeLines(paste0("-------------"), file_conn)
  writeLines(paste0("Biz Category: ", row_data$biz_category), file_conn)
  writeLines(paste0("AI Biz Explanation: ", row_data$biz_explanation), file_conn)
   writeLines(paste0("-------------"), file_conn)
  writeLines(paste0("Voter Category: ", row_data$voter_category), file_conn)
  writeLines(paste0("AI Voter Explanation: ", row_data$voter_explanation), file_conn)
   writeLines(paste0("-------------"), file_conn)
  writeLines(paste0("Politics Category: ", row_data$politics_category), file_conn)
  writeLines(paste0("AI Politics Explanation: ", row_data$politics_explanation), file_conn)
   writeLines(paste0("-------------"), file_conn)
  # Wrap the full text
  wrapped_text <- strwrap(row_data$full_text, width = 80)
  wrapped_text[1] <- paste0("Article Text: ", wrapped_text[1])
  writeLines(wrapped_text, file_conn)
  
  if (i < nrow(validate)) {
    writeLines("\n==================================================\n", file_conn)
  }
}

close(file_conn)
```


 check below to see if tighter was created in the blocks below
 otherwise, create a new copy, save this file as notes and declare victory
 
 validate_new seems to be the new master file, double check for bullshit

#The Timeline Visualization Script

```{r}
# 1. Prepare the data for plotting
plot_data <- final_database %>%
  # Split the categories into individual rows
  separate_rows(category, sep = ";") %>%
  mutate(category = str_trim(category)) %>%
  # Filter to focus on the core themes (optional: remove 'other')
  filter(category %in% c("business", "labor", "economy")) %>%
  # Ensure the date column is a Date object and floor it to the start of the month
  mutate(
    date = as.Date(date),
    month = floor_date(date, "month")
  ) %>%
  # Count occurrences of each category per month
  count(month, category)

# 2. Create the Timeline Plot
ggplot(plot_data, aes(x = month, y = n, color = category, group = category)) +
  # Add points and lines
  geom_line(size = 1.2, alpha = 0.7) +
  geom_point(size = 3) +
  # Formatting the scales
  scale_x_date(date_breaks = "1 month", date_labels = "%b") +
  scale_color_manual(values = c(
    "business" = "#2C3E50", # Dark Blue
    "labor" = "#E74C3C",    # Red
    "economy" = "#27AE60"   # Green
  )) +
  # Labels and Theme
  labs(
    title = "Coverage Trends in 1956",
    subtitle = "Monthly frequency of mentions by category",
    x = "Month of 1956",
    y = "Number of Articles",
    color = "Category"
  ) +
  theme_minimal() +
  theme(
    legend.position = "bottom",
    plot.title = element_text(face = "bold", size = 16),
    panel.grid.minor = element_blank()
  )
```



#-------OLDER -------------------


```{r}
final_classification <- results_raw |>
  separate(raw_output, 
           into = c("new_filename", "category", "explanation"), 
           sep = ",", 
           extra = "merge")
```




#Process results

```{r}
process_llm_response_to_df <- function(response) {
  # Extract lines
  lines <- strsplit(response, "\n")[[1]]
  
  # Remove markdown code block markers if present
  lines <- lines[!grepl("^```", lines)]
  
  # Initialize vectors for data
  filenames <- c()
  categories <- c()
  explanations <- c()
  
  # Flag to track if we're processing data (after header)
  header_found <- FALSE
  
  for (line in lines) {
    # Skip empty lines
    if (trimws(line) == "") next
    
    # Skip row numbers or other artifacts (lines with asterisks)
    if (grepl("\\*\\*", line)) next
    
    # Check if this is the header line
    if (grepl("filename.*category.*explanation", line, ignore.case = TRUE)) {
      header_found <- TRUE
      next
    }
    
    # Process data lines (only after header is found)
    if (header_found || grep("batch.*\\.txt", line)) {
      # Parse each row with better handling of commas within explanations
      parts <- strsplit(line, ",\\s*", perl = TRUE, fixed = FALSE)[[1]]
      
      if (length(parts) >= 1) {
        filename <- parts[1]
        category <- ifelse(length(parts) >= 2, parts[2], "")
        
        # Handle the explanation (everything after second comma)
        if (length(parts) >= 3) {
          explanation <- paste(parts[3:length(parts)], collapse = ", ")
        } else {
          explanation <- NA
        }
        
        filenames <- c(filenames, filename)
        categories <- c(categories, category)
        explanations <- c(explanations, explanation)
      }
    }
  }
  
  # Create and return the dataframe
  if (length(filenames) > 0) {
    data.frame(
      filename = filenames,
      category = categories,
      explanation = explanations,
      stringsAsFactors = FALSE
    )
  } else {
    # Return empty dataframe with correct structure if no data found
    data.frame(
      filename = character(0),
      category = character(0),
      explanation = character(0),
      stringsAsFactors = FALSE
    )
  }
}
lat_1956_biz <- process_llm_response_to_df(biz)
write.csv(lat_1956_biz, "./output/ai_biz_2_jan_8_2025.csv")
```


count the results
```{r}
lat_1956_politics |> 
  count(category) |> 
  arrange(desc(n))

#politics:
# 1    other 20
# 2 politics 88
# voter_turnout	54			
# other	52	
# other	33			
# labor classification	26			
# economy	19			
# economy;labor classification	9			
# business	8			
# business;labor classification	7			
# business;economy	4			
# business;economy;labor classification	2	

#tighter = 3 or more
# politics	81			
# other	27	
# other	58			
# voter_turnout	50	
# other	28			
# economy	10			
# business	7			
# business;economy	7			
# labor	5			
# economy;labor	2			
# 1			
# business;economy;labor	1			
# business;labor	1	

```

#Compare the results
```{r}
july24 <- rio::import("https://docs.google.com/spreadsheets/d/1Y-IWU_AgbyE-2G2jyT15MIO2jtv_Qpgi1imRwKTjPHQ/edit?gid=1373544130#gid=1373544130", which = "July24_results", header = TRUE) |> 
  clean_names()

oct20 <- rio::import("https://docs.google.com/spreadsheets/d/1Y-IWU_AgbyE-2G2jyT15MIO2jtv_Qpgi1imRwKTjPHQ/edit?gid=1553901874#gid=1553901874", which = "Oct20_results", header = TRUE) |> 
  clean_names() 


```


### Process to join
Politics
```{r}
july24_clean <- july24 |> 
  select(filename, category, explanation, correct, human_comments) |> 
  rename(july24_category = category, july24_explanation = explanation, july24_correct = correct, july24_human_comments = human_comments)
oct20_clean <- oct20 |> 
  select(filename, category, explanation) |> 
  rename(oct20_category = category, oct_20explanation = explanation)


#change variable names for voter, politics etc
jan_7 <- lat_1956_biz |> 
   rename(jan7_category = category, jan7_explanation = explanation)

combo <- oct20_clean |> 
  right_join(july24_clean, by ="filename") |> 
  right_join(jan_7, by = "filename")


#split crime1 into three new columns
combo <- separate(data = combo, col = jan7_category, into = c("jan7_category1", "jan7_category2"), sep = ";", extra = "merge", fill = "right")
combo <- separate(data = combo, col = oct20_category, into = c("Oct20_category1", "Oct20_category2"), sep = ";", extra = "merge", fill = "right")
combo <- separate(data = combo, col = july24_category, into = c("july24_category1", "july24_category2"), sep = ";", extra = "merge", fill = "right")




# combo <- jan_7 |> 
#   right_join(combo, by ="filename")


```



### Quick view of any entry by row
```{r}
wrapped_text <- strwrap(as.character(combo$jan7_explanation[92]), width = 60)
writeLines(wrapped_text, "temp_text.txt")
file.edit("temp_text.txt")
```


### Analyze differences
```{r}
diffs_biz <- combo |> 
  mutate(changed_july24 = case_when(
    jan7_category1 == july24_category1 ~ "same",
    jan7_category1 != july24_category1 ~ "different",
    jan7_category2 == july24_category2 ~ "same",
    jan7_category2 != july24_category2 ~ "different",
    .default = NA_character_
  )) |> 
    mutate(changed_oct20 = case_when(
    jan7_category1 == Oct20_category1 ~ "same",
    jan7_category1 != Oct20_category1 ~ "different",
    jan7_category2 == Oct20_category2 ~ "same",
    jan7_category2 != Oct20_category2 ~ "different",
    .default = NA_character_
  )) |> 
  
  select(changed_july24, jan7_category1, jan7_category2, july24_category1, jan7_category1, jan7_category2, july24_category2, changed_oct20, jan7_category1, jan7_category2, Oct20_category1, Oct20_category2, july24_correct, july24_human_comments, everything())

write_csv(diffs_biz, "./output/jan7_biz_july24_diffs.csv")
```

```{r}
diffs_voter <- read_csv("./output/jan7_voter_july24_diffs.csv")
diffs_biz <- read_csv("./output/jan7_biz_july24_diffs.csv")

```


### Count categories
```{r}

current_counts <- combo |>
  select(filename, jan7_category1, jan7_category2) |>
  pivot_longer(cols = c(jan7_category1, jan7_category2), 
               names_to = "category_type", 
               values_to = "category") |>
  filter(!is.na(category)) |>
  count(category, name = "current_count")

# Count all july24_category1 and july24_category2 together
oct20_counts <- combo |>
  select(filename, Oct20_category1, Oct20_category2) |>
  pivot_longer(cols = c(Oct20_category1, Oct20_category2), 
               names_to = "category_type", 
               values_to = "category") |>
  filter(!is.na(category)) |>
  count(category, name = "Oct20_count")

# Count all july24_category1 and july24_category2 together
july24_counts <- combo |>
  select(filename, july24_category1, july24_category2) |>
  pivot_longer(cols = c(july24_category1, july24_category2), 
               names_to = "category_type", 
               values_to = "category") |>
  filter(!is.na(category)) |>
  count(category, name = "july24_count")



# comparison_voter <- comparison



comparison_biz <- list(current_counts, oct20_counts, july24_counts) |> 
  reduce(full_join, by = "category") |> 
  arrange(desc(current_count))

# # Combine them side by side
# comparison_biz <- current_counts |> 
#   full_join(oct20_counts, by = "category") |> 
#   full_join(july24_counts, by = "category") |> # Now it's properly included
#   replace_na(list(current_count = 0, Oct20_count = 0, july24_count = 0)) |> 
#   arrange(desc(current_count))
```

#-----------------------------------
### Validate data
#-----------------------------------
Combine dfs
```{r}
biz <- lat_1956_biz |> 
  rename(biz_category = category, biz_explanation = explanation)
voter <- lat_1956_voter |> 
  rename(voter_category = category, voter_explanation = explanation)
politics <- lat_1956_politics |> 
  rename(politics_category = category, politics_explanation = explanation)

validate <- list(biz, voter, politics) |> 
  reduce(full_join, by = "filename")

```





### Combine dfs
```{r}


validate <- validate |> 
  inner_join(tighter, by=c("filename"="new_filename"))

validate <- validate |> 
  select(filename, date, year, title, full_text, everything())

validate_brief <- validate |> 
  select(filename, date, year, title, full_text, biz_category, biz_explanation, voter_category, voter_explanation, politics_category, politics_explanation) |> 
  mutate(correct_y_n = "")

write_csv(validate_brief, "./output/validate_brief_update_jan7.csv")

```

Print out articles for verification
```{r}

# Now create the text file with locations highlighted
file_conn <- file("ai_classifier_moley_verify.txt", "w")

for (i in 1:nrow(validate)) {
  row_data <- validate[i, ]
  
  writeLines(paste0("Document ID: ", row_data$filename), file_conn)
  writeLines(paste0("Date: ", row_data$date), file_conn)
  writeLines(paste0("Headline: ", row_data$title), file_conn)
  writeLines(paste0("-------------"), file_conn)
  writeLines(paste0("Biz Category: ", row_data$biz_category), file_conn)
  writeLines(paste0("AI Biz Explanation: ", row_data$biz_explanation), file_conn)
   writeLines(paste0("-------------"), file_conn)
  writeLines(paste0("Voter Category: ", row_data$voter_category), file_conn)
  writeLines(paste0("AI Voter Explanation: ", row_data$voter_explanation), file_conn)
   writeLines(paste0("-------------"), file_conn)
  writeLines(paste0("Politics Category: ", row_data$politics_category), file_conn)
  writeLines(paste0("AI Politics Explanation: ", row_data$politics_explanation), file_conn)
   writeLines(paste0("-------------"), file_conn)
  # Wrap the full text
  wrapped_text <- strwrap(row_data$full_text, width = 80)
  wrapped_text[1] <- paste0("Article Text: ", wrapped_text[1])
  writeLines(wrapped_text, file_conn)
  
  if (i < nrow(validate)) {
    writeLines("\n==================================================\n", file_conn)
  }
}

close(file_conn)
```

#-----------------------------------
### Analyze differences
#-----------------------------------
```{r}
diffs <- combo |> 
  mutate(changed = case_when(
    category1 == july24_category1 ~ "same",
    category1 != july24_category1 ~ "different",
     category2 == july24_category2 ~ "same",
    category2 != july24_category2 ~ "different",
    .default = NA_character_
  )) |> 
  select(changed, category1, july24_category1, category2, july24_category2, july24_correct, july24_human_comments, everything())

write_csv(diffs, "./output/oct20_july24_diffs.csv")
```


### Count all category1 and category2 together
```{r}

current_counts <- combo |>
  select(filename, category1, category2) |>
  pivot_longer(cols = c(category1, category2), 
               names_to = "category_type", 
               values_to = "category") |>
  filter(!is.na(category)) |>
  count(category, name = "current_count")

# Count all july24_category1 and july24_category2 together
july24_counts <- combo |>
  select(filename, july24_category1, july24_category2) |>
  pivot_longer(cols = c(july24_category1, july24_category2), 
               names_to = "category_type", 
               values_to = "category") |>
  filter(!is.na(category)) |>
  count(category, name = "july24_count")

# Combine them side by side
comparison <- full_join(current_counts, july24_counts, by = "category") |>
  replace_na(list(current_count = 0, july24_count = 0)) |>
  arrange(desc(current_count))

comparison





```

```{r}
diffs |> 
  count(changed)


```

### Tally the categories
```{r}
left_join(
  diffs |> count(category, name = "category_count"),
  diffs |> count(july24_category, name = "july24_count"),
  by = c("category" = "july24_category")
)

```




#-----------------------------------
# OLDER Versions
#-----------------------------------



Bridget prompt

```{r}
chat2 <- chat_google_gemini(
  system_prompt = "You are an academic researcher performing context analysis on selected news articles. Analyze each article and classify it based on specified criteria.

In this prompt, the phrases “category” and “classification” and any of their grammatical variations are synonymous. 

An article should receive a classification if it meets the requirements for that category. An article can be as many categories as you feel it applies to. It can fall under more than one category. Assign all applicable classifications separated by semicolons, and list classifications in alphabetical order for consistency. Example: An article with 3 mentions of electoral politics AND 2 mentions of business issues would be classified as 'business;politics'

Each article must independently meet a threshold of two or more mentions of specified criteria to be included or considered a specific category.

If an article meets none of the criteria, classify it as 'other'

—-Start Categories Criteria—---

POLITICS: an article contains, in text, content, or theme, two or more of the following

- Voting in a political election
- Upcoming elections (primaries, general elections, special elections)
- Election results and outcomes
- Political campaigns
- Political campaign strategies
- Candidate announcements, debates, or endorsements
- Election polling and predictions
- Political party activities related to elections
- Specific words: “election”, “vote”, “polls”, “ballots”, “candidate”


VOTER TURNOUT: an article contains two or more,  in text, content, or theme, mentions of 
Amount of people participating in voting during an election
Voter registration drives or registration statistics
Early voting, absentee voting, or mail-in ballot usage
Voter turnout rates or participation levels
Get-out-the-vote (GOTV) campaigns or efforts
Barriers to voting or voter access issues (polling locations, ID requirements, wait times)
Demographic breakdowns of voter participation
Voter suppression
Numerical quantities, statistics, or values related to or describing the amount of people or members of a group, community, or place participating in an election

ECONOMY:  an article contains two or more,  in text, content, or theme, mentions of 
Macroeconomic issues or economic policy.
Macroeconomic indicators (Examples: GDP, inflation, unemployment rates, economic growth)
Monetary policy (Federal Reserve actions, interest rates)
Policy that directly involves with the economy
Trade policy (Examples: tariffs, trade agreements, import/export regulations)
Economic forecasts or recession/expansion predictions
Currency markets and exchange rates
National or global economic conditions and trends

BUSINESS: an article contains two or more, in text, content, or theme, mentions of 
Companies, Corporate entities, their operations, or strategic decisions
Executives, Business leaders, appointments, departures, or leadership actions
Product launches and announcements
Marketing campaigns
Regulatory compliance matters
Mergers and acquisitions
Partnerships and collaborations between companies or other industry groups
Corporate strategy changes
Financial Dealings common to business (examples: Earnings, investments, funding, stock performance, financial results)
Industry, Sector trends, market analysis, competitive dynamics
Terms as 'private enterprise', 'company', 'firm', 'business leaders', 'businessmen',

LABOR CLASSIFICATION: an article contains two or more, in text, content, or theme,

Strikes or work stoppages
Unionization efforts
Union elections
Worker disputes involving unions or collective bargaining
Public policy issues focusing on organized labor (Examples: llabor law reforms, right-to-work legislation)
Statements or actions by union leaders or labor organizations
Terms such as 'AFL' and or 'CIO' (Congress of Industrial Organizations)

For the above categories, there are some topics that could create a classification “gray area”. For the purposes of this research, use the following descriptions to validate classifications.  Any article that any of these apply to can still be categorized as multiple categories.

If the article discusses, in text, theme, or content, policy debates or legislation without electoral context, then it can be marked as 'other', among any other applicable categories
If the article discusses, in text, theme, or content, appointed officials or bureaucratic actions, then it is not ‘politics’ category unless the discussion is tied to an election
If the article discusses, in text, theme, or content, individual company financial performance, classify it as 'business', among any other applicable categories
If the article discusses, in text, theme, or content, industry-specific trends without macroeconomic context → classify as 'business'
If the article discusses, in text, theme, or content, stock market movements alone without broader economic analysis or context, classify it as 'business', among any other applicable categories
If the article discusses, in text, theme, or content, fiscal policy debates over taxation and spending in Congress, classify it as 'politics', among any other applicable categories
If the article discusses, in text, theme, or content, labor issues such as strikes, unionization, worker disputes, classify it as ‘labor’, not ‘business’, among any other applicable categories
If the article only mentions a company tangentially (e.g., 'Apple CEO attended a charity gala') without discussing business matters, it does not fall under ‘business’


—-End Categories Criteria—---


Return ONLY a CSV with exactly THREE columns and NO additional text:

Column 1: new_filename (the article identifier)
Column 2: category (one or more classifications separated by semicolons)
Column 3: explanation (brief justification citing specific counts)

- Include a header row: new_filename,category,explanation
- No quotes around values unless they contain commas
- Multiple categories in alphabetical order separated by semicolons
- Explanation must specify the count for each assigned category
- Maximum 15 words per explanation

Examples:
article1.txt,politics,`3 mentions of election campaigns, 2 candidate endorsements`
article2.txt,business;economy,`4 company strategy mentions, 2 GDP references'
article3.txt,other, `No categories met the 2-mention threshold.” 

No other explanation is required for “other”.)

```






## Chat3 ver 10-20-2025
```{r}
chat3 <- chat_google_gemini(
  system_prompt = "You are an academic researcher performing context analysis on selected news articles. Analyze each article and classify it based on these criteria,
  
  1. POLITICS classification: Classify an article as 'politics' if it contains two or more mentions of electoral politics.

'Electoral politics' is defined as:
- Upcoming elections (primaries, general elections, special elections)
- Election results and outcomes
- Political campaigns and campaign strategies
- Candidate announcements, debates, or endorsements
- Election polling and predictions
- Political party activities related to elections
- **Terms**: Classify an article as 'politics' if it contains the issues above and also mentions terms such as 'vote' or 'precinct' or 'primary results'

EXCLUSIONS:
- Policy debates or legislation without electoral context → classify as 'other'
- Appointed officials or bureaucratic actions → not electoral politics unless tied to an election


2. VOTER TURNOUT Classification: 
Classify an article as 'voter_turnout' if it contains two or more mentions of voter participation or turnout-related issues.

'Voter turnout' is defined as:
- Voter registration drives or registration statistics
- Early voting, absentee voting, or mail-in ballot usage
- Voter turnout rates or participation levels
- Get-out-the-vote (GOTV) campaigns or efforts
- Barriers to voting or voter access issues (polling locations, ID requirements, wait times)
- Demographic breakdowns of voter participation
- Voter suppression
- **Terms**: Classify an article as 'voter_turnout' if it contains the issues above and also mentions terms such as 'ballot box'

  3. ECONOMY classification: Classify an article as 'economy' if it contains two or more mentions of macroeconomic issues or economic policy.

'Economy' is defined as:
- Macroeconomic indicators (GDP, inflation, unemployment rates, economic growth)
- Monetary policy (Federal Reserve actions, interest rates)
- Trade policy (tariffs, trade agreements, import/export regulations)
- Economic forecasts or recession/expansion predictions
- Currency markets and exchange rates
- National or global economic conditions and trends

EXCLUSIONS:
- Individual company financial performance → classify as 'business'
- Industry-specific trends without macroeconomic context → classify as 'business'
- Stock market movements alone (unless tied to broader economic analysis) → classify as 'business'
- Fiscal policy debates over taxation and spending in Congress  → classify as 'politics'

  4. BUSINESS classification: Classify an article as 'business' if it contains two or more mentions of business issues.
  
BUSINESS ISSUES is defined as articles that primarily discuss:
- **Companies**: Corporate entities, their operations, or strategic decisions
- **Executives**: Business leaders, appointments, departures, or leadership actions
- **Business Activity**: Including but not limited to:
  - Product launches and announcements
  - Marketing campaigns
  - Regulatory compliance matters
  - Mergers and acquisitions
  - Partnerships and collaborations
  - Corporate strategy changes
- **Financial Dealings**: Earnings, investments, funding, stock performance, financial results
- **Industry**: Sector trends, market analysis, competitive dynamics
- **Terms**: Classify an article as 'business' if it contains the issues above and also mentions such terms as 'private enterprise', 'company', 'firm', 'business leaders', 'businessmen',

EXCLUSIONS:
- Labor issues (strikes, unionization, worker disputes) should be classified separately as LABOR, not business issues
- Articles that only mention a company tangentially (e.g., 'Apple CEO attended a charity gala') without discussing business matters

  5.LABOR CLASSIFICATION: Classify an article as 'labor' if it contains two or more mentions of organized labor issues.

'Organized labor' is defined as:
- Strikes or work stoppages
- Unionization efforts or union elections
- Worker disputes involving unions or collective bargaining
- Public policy issues focusing on organized labor (e.g., labor law reforms, right-to-work legislation)
- Statements or actions by union leaders or labor organizations

- **Terms**: Classify an article as 'labor' if it contains the issues above and also mentions terms such as 'AFL' and or 'CIO' (Congress of Industrial Organizations),

IMPORTANT:
- The threshold is two or more mentions to avoid misclassifying articles that only reference labor tangentially
- General workplace issues (individual employee disputes, non-union worker complaints, HR policies) do NOT count as organized labor unless unions are involved

6. OVERLAPPING CLASSIFICATIONS:
An article should receive multiple classifications if it meets the threshold 
(two or more mentions) for more than one category.

- Assign all applicable classifications separated by semicolons
- List classifications in alphabetical order for consistency
- Example: An article with 3 mentions of electoral politics AND 2 mentions 
  of business issues would be classified as 'business;politics'


COUNTING METHODOLOGY:
- Count distinct mentions, not repeated references to the same fact
- A single sentence can contain multiple mentions if it discusses 
  multiple distinct aspects of a category
- When in doubt, count conservatively


EDGE CASES:
- If an article has exactly 2 mentions but you're uncertain if they're 
  distinct enough, err on the side of inclusion
- If an article discusses the same election/company/policy throughout, 
  count each substantive new point, not repetitions
- Introductory context-setting doesn't count toward thresholds

**Terms**: An article must contain BOTH the substantive issues described 
above AND at least one of these terms to qualify for this classification.

IMPORTANT: Each category must independently meet its own threshold of 
two or more mentions to be included in the classification.
  
  7. If an article meets none of the criteria, classify it as 'other'
  
 REQUIRED OUTPUT FORMAT:
Return ONLY a CSV with exactly THREE columns and NO additional text:

Column 1: new_filename (the article identifier)
Column 2: category (one or more classifications separated by semicolons)
Column 3: explanation (brief justification citing specific counts)

Rules:
- Include a header row: new_filename,category,explanation
- No quotes around values unless they contain commas
- Multiple categories in alphabetical order separated by semicolons
- Explanation must specify the count for each assigned category
- Maximum 15 words per explanation

Examples:
article1.txt,politics,`3 mentions of election campaigns, 2 candidate endorsements`
article2.txt,business;economy,`4 company strategy mentions, 2 GDP references'
article3.txt,other, `No categories met 2-mention threshold` 
  No additional text, explanations, or summary counts.")


```
  
### chat4 new prompt 10-21-2025

```{r}
chat4 <- chat_google_gemini(
  system_prompt = "You are an academic researcher performing content analysis on newspaper articles. 
Your task is to classify each article based on specific criteria defined below.

COUNTING METHODOLOGY:
- Count distinct mentions, not repeated references to the same fact
- A single sentence can contain multiple mentions if it discusses multiple distinct aspects of a category
- When in doubt, count conservatively
- Introductory context-setting does not count toward thresholds
- Each substantive new point counts; mere repetition does not

=============================================================================
CLASSIFICATION CATEGORIES (alphabetically)
=============================================================================

1. BUSINESS CLASSIFICATION

Classify an article as 'business' if it contains two or more mentions of business issues.

Business issues include articles that primarily discuss:
- Companies: Corporate entities, their operations, or strategic decisions
- Executives: Business leaders, appointments, departures, or leadership actions
- Business Activity:
  * Product launches and announcements
  * Marketing campaigns
  * Regulatory compliance matters
  * Mergers and acquisitions
  * Partnerships and collaborations
  * Corporate strategy changes
- Financial Dealings: Earnings, investments, funding, stock performance, financial results
- Industry: Sector trends, market analysis, competitive dynamics

**Indicator Terms**: 'private enterprise', 'company', 'firm', 'business leaders', 'businessmen', 'corporation', 'CEO', 'revenue'

EXCLUSIONS:
- Labor issues (strikes, unionization, worker disputes) → classify as 'labor'
- Articles that only mention a company tangentially without discussing business matters
- Macroeconomic policy discussions → classify as 'economy'

---

2. ECONOMY CLASSIFICATION

Classify an article as 'economy' if it contains two or more mentions of macroeconomic issues or economic policy.

Economy issues include:
- Macroeconomic indicators: GDP, inflation, unemployment rates, economic growth
- Monetary policy: Federal Reserve actions, interest rates, money supply
- Trade policy: Tariffs, trade agreements, import/export regulations
- Economic forecasts or recession/expansion predictions
- Currency markets and exchange rates
- National or global economic conditions and trends
- Economic crises or systemic economic issues

**Indicator Terms**: 'GDP', 'inflation', 'Federal Reserve', 'interest rates', 'recession', 'economic growth', 'unemployment rate'

EXCLUSIONS:
- Individual company financial performance → classify as 'business'
- Industry-specific trends without macroeconomic context → classify as 'business'
- Stock market movements alone (unless tied to broader economic analysis) → classify as 'business'
- Fiscal policy debates over taxation and spending in Congress → classify as 'politics'

---

3. LABOR CLASSIFICATION

Classify an article as 'labor' if it contains two or more mentions of organized labor issues.

Organized labor issues include:
- Strikes or work stoppages
- Unionization efforts or union elections
- Worker disputes involving unions or collective bargaining
- Labor contract negotiations
- Public policy issues focusing on organized labor (e.g., labor law reforms, right-to-work legislation)
- Statements or actions by union leaders or labor organizations
- Picket lines, labor protests, or organizing campaigns

**Indicator Terms**: 'union', 'strike', 'collective bargaining', 'picket line', 'AFL-CIO', 'labor organization', 'workers' rights', 'unionization'

Note: `CIO` refers to Congress of Industrial Organizations (historical labor federation, now part of AFL-CIO)

EXCLUSIONS:
- General workplace issues (individual employee disputes, non-union worker complaints, HR policies) without union involvement
- Executive/management labor issues → classify as 'business'

---

4. POLITICS CLASSIFICATION

Classify an article as 'politics' if it contains two or more mentions of electoral politics.

Electoral politics includes:
- Upcoming elections (primaries, general elections, special elections, referendums)
- Election results and outcomes
- Political campaigns and campaign strategies
- Candidate announcements, debates, or endorsements
- Election polling and predictions
- Political party activities related to elections
- Voter mobilization efforts tied to specific elections
- Campaign finance in electoral context

**Indicator Terms**: 'vote', 'election', 'candidate', 'primary', 'ballot', 'campaign', 'precinct', 'primary results', 'polling'

EXCLUSIONS:
- Policy debates or legislation without electoral context → classify as 'other'
- Appointed officials or bureaucratic actions → not electoral politics unless tied to an election
- Governance and policy implementation → classify as 'other'

---

5. VOTER TURNOUT CLASSIFICATION

Classify an article as 'voter_turnout' if it contains two or more mentions of voter participation or turnout-related issues.

Voter turnout issues include:
- Voter registration drives or registration statistics
- Early voting, absentee voting, or mail-in ballot usage
- Voter turnout rates or participation levels
- Get-out-the-vote (GOTV) campaigns or efforts
- Barriers to voting or voter access issues (polling locations, ID requirements, wait times)
- Voter suppression allegations or concerns
- Demographic breakdowns of voter participation
- Voting infrastructure (polling places, voting machines, ballot access)

**Indicator Terms**: 'ballot box', 'voter registration', 'turnout rate', 'early voting', 'absentee ballot', 'polling place', 'voter access'

=============================================================================
OVERLAPPING CLASSIFICATIONS
=============================================================================

An article may qualify for multiple classifications if it independently meets 
the two-mention threshold for more than one category.

PROCESS:
a) Evaluate the article against each classification independently
b) Count mentions for each category separately
c) Assign ALL categories that meet the threshold (2+ mentions)
d) List multiple classifications alphabetically, separated by semicolons

EXAMPLES:
- Article discusses 3 campaign events + 2 corporate mergers → 'business;politics'
- Article discusses 4 election issues + 3 GDP mentions + 2 strikes → 'economy;labor;politics'
- Article discusses 1 election + 5 business issues → 'business' (politics doesn't meet threshold)
- Article discusses 3 voter registration drives + 2 election debates → 'politics;voter_turnout'

IMPORTANT: Do not blend counts across categories. Each category stands alone.

=============================================================================
EDGE CASES
=============================================================================

- If an article has exactly 2 mentions but you're uncertain if they're distinct enough, err on the side of inclusion
- If an article discusses the same election/company/policy throughout, count each substantive new point, not repetitions
- If multiple categories could apply to the same content, count it for each relevant category independently

=============================================================================
DEFAULT CLASSIFICATION
=============================================================================

If an article meets none of the criteria above (does not reach the two-mention 
threshold for any category), classify it as 'other'.

=============================================================================
REQUIRED OUTPUT FORMAT
=============================================================================

Return ONLY a CSV with exactly THREE columns and NO additional text:

Column 1: new_filename (the article identifier)
Column 2: category (one or more classifications separated by semicolons)
Column 3: explanation (brief justification citing specific counts)

FORMATTING RULES:
- Include a header row: new_filename,category,explanation
- No quotes around values unless they contain commas
- Multiple categories in alphabetical order separated by semicolons (no spaces)
- Explanation must specify the count for each assigned category
- Maximum 20 words per explanation
- Do not include any summary statistics, commentary, or additional text

EXAMPLES:

new_filename,category,explanation
article1.txt,politics,3 mentions of election campaigns and 2 candidate endorsements
article2.txt,business;economy,4 company strategy mentions and 2 GDP references
article3.txt,voter_turnout,2 voter registration drives and 3 early voting statistics
article4.txt,labor;politics,3 strike references and 2 election campaign mentions
article5.txt,other,No categories met 2-mention threshold

=============================================================================

Begin classification now.")
```


#------------------------------------------------------


```{r}
july24_clean <- july24 |> 
  select(filename, category, explanation, correct, human_comments) |> 
  rename(july24_category = category, july24_explanation = explanation, july24_correct = correct, july24_human_comments = human_comments)
oct20_clean <- oct20 |> 
  select(filename, category, explanation)

combo <- oct20_clean |> 
  right_join(july24_clean, by ="filename")

#split crime1 into three new columns
combo <- separate(data = combo, col = category, into = c("category1", "category2"), sep = ";", extra = "merge", fill = "right")
combo <- separate(data = combo, col = july24_category, into = c("july24_category1", "july24_category2"), sep = ";", extra = "merge", fill = "right")
```



#Notes

Prompt guidance from Claude.ai
Suggested Prompt Structure
You are analyzing news articles to identify and categorize business issues.

BUSINESS ISSUES are defined as articles that primarily discuss:
- **Companies**: Corporate entities, their operations, or strategic decisions
- **Executives**: Business leaders, appointments, departures, or leadership actions
- **Business Activity**: Including but not limited to:
  - Product launches and announcements
  - Marketing campaigns
  - Regulatory compliance matters
  - Mergers and acquisitions
  - Partnerships and collaborations
  - Corporate strategy changes
- **Financial Dealings**: Earnings, investments, funding, stock performance, financial results
- **Industry**: Sector trends, market analysis, competitive dynamics

EXCLUSIONS:
- Labor issues (strikes, unionization, worker disputes) should be classified separately as LABOR, not business issues
- Articles that only mention a company tangentially (e.g., "Apple CEO attended a charity gala") without discussing business matters

TASK:
For each article, determine:
1. Does it contain a business issue? (YES/NO)
2. If YES, what is the primary category? (Company, Executive, Business Activity, Financial, Industry)
3. Provide a brief justification (1 sentence)



#old prompt


#used this prompt
```{r}
chat2 <- chat_google_gemini(
  system_prompt = "You are an academic researcher performing context analysis on selected Newsweek articles. Analyze each article and classify it based on these criteria:
  
  1. If an article contains two or more mentions of an upcoming election or electoral politics, classify it as 'politics'
  2. If an article contains two or more mentions of vote or voter registration, classify it as 'voter_turnout'
  3. If an article contains two or more mentions the economic developments, classify it as 'economy'
  4. If an article contains two or more mentions of business issues, classify it as 'business'
  5. If an article meets multiple criteria, assign multiple categories separated by semicolons
  6. If an article meets none of the criteria, classify it as 'other'
  
  Return ONLY a CSV-formatted result with exactly THREE (3) columns:
  filename, category, explanation
  
  For example:
  filename, category, explanation
  article1.txt,politics, warning about upcoming election
  article2.txt,democrat_critique, these words were critical of democrats: xyz
  article3.txt,business;politics, business mentioned three times voter turnout twice
  article4.txt,other
  
  No additional text, explanations, or summary counts."
)

# Send to the LLM
politics <- chat2$chat(combined_text_with_filenames)
```
