---
title: "R Notebook"
output: null
---

```{r}
#install.packages("ellmer")
library(ellmer)
library(tidyverse)
library(glue)
library(janitor)

#Sys.setenv(GOOGLE_API_KEY = "")

```

#Check Gemini is working

```{r}
chat <- chat_gemini()

chat$chat("Tell me three jokes about journalists")
```
# LAT Data
## Load LAT Data
```{r echo = F}
#2501 articles in index
lat_article_index <-  rio::import("/Users/gizmofo/Library/CloudStorage/Dropbox/Current_Projects/Moley project 2024/Indexes of Moley Articles/lat_txt_index_renamed_7_23.csv") |> 
  clean_names() |> 
  mutate(year = lubridate::year(date))
  

#284067 rows of text
lat_articles_text <-  read_csv("/Users/gizmofo/Library/CloudStorage/Dropbox/Current_Projects/Moley project 2024/Indexes of Moley Articles/moley_lat_text_june_21.csv") |>
   clean_names() |>
    mutate(year = as.numeric(year))

# lat_articles_text <- experiment
```


```{r}
#1956 articles: 14,218 lines
llm_lat <- lat_articles_text[126052:140269, ]

llm_lat <- llm_lat |> 
  mutate(sentence = gsub("\n", " ", sentence)) |> 
  mutate(sentence = gsub("\\s+", " ", sentence))

```

```{r}
process_articles <- function(df) {
  # First group by article identifiers and concatenate sentences
  # Using filename as the identifier, but you might need to use other columns
  compiled_df <- df %>%
    group_by(filename) %>%
    summarize(
      sentence = paste(na.omit(sentence), collapse = " "),
      title = first(title),
      abstract = first(abstract),
      authors = first(authors),
      filepath = first(filepath),
      index = first(index),
      issn = first(issn),
      pages = first(pages),
      title = first(title),
      year = first(year),
      document_url = first(document_url),
      find_a_copy = first(find_a_copy),
      date = first(date),
      year=first(year)
    )
  
  # Remove punctuation and spaces from the sentence column
  compiled_df <- compiled_df %>%
    mutate(sentence = str_replace_all(sentence, "[[:punct:][:space:]]", "")) |> 
    mutate(sentence = tolower(sentence))
  
  return(compiled_df)
}

# Make sure to load the necessary libraries
library(dplyr)
library(stringr)

# Apply the function to your dataframe
processed_llm_test <- process_articles(llm_lat)
```

```{r}
# Prepare data with filenames and content
articles_for_analysis <- processed_llm_test %>%
  select(filename, sentence) %>%
  mutate(article_data = paste("FILENAME:", filename, "\nCONTENT:", sentence))

# Combine with clear separators
combined_text_with_filenames <- paste(articles_for_analysis$article_data, 
                                    collapse = "\n\n---ARTICLE SEPARATOR---\n\n")
```

# LLM Prompt
ver 10-1-2025
```{r}
chat2 <- chat_gemini(
  system_prompt = "You are an academic researcher performing context analysis on selected Newsweek articles. Analyze each article and classify it based on these criteria:
  
  1. POLITICS classification: Classify an article as 'POLITICS' if it contains two or more mentions of electoral politics.

'Electoral politics' is defined as:
- Upcoming elections (primaries, general elections, special elections)
- Election results and outcomes
- Political campaigns and campaign strategies
- Candidate announcements, debates, or endorsements
- Election polling and predictions
- Political party activities related to elections

EXCLUSIONS:
- Policy debates or legislation without electoral context → classify as 'other'
- Appointed officials or bureaucratic actions → not electoral politics unless tied to an election


2. VOTER TURNOUT Classification: 
Classify an article as 'voter_turnout' if it contains two or more mentions of voter participation or turnout-related issues.

'Voter turnout' is defined as:
- Voter registration drives or registration statistics
- Early voting, absentee voting, or mail-in ballot usage
- Voter turnout rates or participation levels
- Get-out-the-vote (GOTV) campaigns or efforts
- Barriers to voting or voter access issues (polling locations, ID requirements, wait times)
- Demographic breakdowns of voter participation

  3. ECONOMY classification: Classify an article as 'economy' if it contains two or more mentions of macroeconomic issues or economic policy.

'Economy' is defined as:
- Macroeconomic indicators (GDP, inflation, unemployment rates, economic growth)
- Monetary policy (Federal Reserve actions, interest rates, money supply)
- Trade policy (tariffs, trade agreements, import/export regulations)
- Fiscal policy (government spending, taxation, budget deficits)
- Economic forecasts or recession/expansion predictions
- Currency markets and exchange rates
- National or global economic conditions and trends

EXCLUSIONS:
- Individual company financial performance → classify as 'business'
- Industry-specific trends without macroeconomic context → classify as 'business'
- Stock market movements alone (unless tied to broader economic analysis) → classify as 'business'

  4. BUSINESS classification: Classify an article as 'business' if it contains two or more mentions of business issues.
  
BUSINESS ISSUES is defined as articles that primarily discuss:
- **Companies**: Corporate entities, their operations, or strategic decisions
- **Executives**: Business leaders, appointments, departures, or leadership actions
- **Business Activity**: Including but not limited to:
  - Product launches and announcements
  - Marketing campaigns
  - Regulatory compliance matters
  - Mergers and acquisitions
  - Partnerships and collaborations
  - Corporate strategy changes
- **Financial Dealings**: Earnings, investments, funding, stock performance, financial results
- **Industry**: Sector trends, market analysis, competitive dynamics

EXCLUSIONS:
- Labor issues (strikes, unionization, worker disputes) should be classified separately as LABOR, not business issues
- Articles that only mention a company tangentially (e.g., 'Apple CEO attended a charity gala') without discussing business matters

  5.LABOR CLASSIFICATION: Classify an article as 'LABOR' if it contains two or more mentions of organized labor issues.

'Organized labor' is defined as:
- Strikes or work stoppages
- Unionization efforts or union elections
- Worker disputes involving unions or collective bargaining
- Public policy issues focusing on organized labor (e.g., labor law reforms, right-to-work legislation)
- Statements or actions by union leaders or labor organizations

IMPORTANT:
- The threshold is two or more mentions to avoid misclassifying articles that only reference labor tangentially
- General workplace issues (individual employee disputes, non-union worker complaints, HR policies) do NOT count as organized labor unless unions are involved

  6. If an article meets multiple criteria, assign multiple categories separated by semicolons. 'Multiple criteria' would mean two mentions of politics AND two mentions of business resulting in the category 'politics;business'
  7. If an article meets none of the criteria, classify it as 'other'
  
  Return ONLY a CSV-formatted result with exactly THREE (3) columns:
  filename, category, explanation
  
  For example:
  filename, category, explanation
  article1.txt,politics, warning about upcoming election
  article2.txt,democrat_critique, these words were critical of democrats: xyz
  article3.txt,business;politics, business mentioned three times voter turnout twice
  article4.txt,other
  
  No additional text, explanations, or summary counts."
)

# Send to the LLM
politics <- chat2$chat(combined_text_with_filenames)
```

#Process results

```{r}
process_llm_response_to_df <- function(response) {
  # Extract lines
  lines <- strsplit(response, "\n")[[1]]
  
  # Remove markdown code block markers if present
  lines <- lines[!grepl("^```", lines)]
  
  # Initialize vectors for data
  filenames <- c()
  categories <- c()
  explanations <- c()
  
  # Flag to track if we're processing data (after header)
  header_found <- FALSE
  
  for (line in lines) {
    # Skip empty lines
    if (trimws(line) == "") next
    
    # Skip row numbers or other artifacts (lines with asterisks)
    if (grepl("\\*\\*", line)) next
    
    # Check if this is the header line
    if (grepl("filename.*category.*explanation", line, ignore.case = TRUE)) {
      header_found <- TRUE
      next
    }
    
    # Process data lines (only after header is found)
    if (header_found || grep("batch.*\\.txt", line)) {
      # Parse each row with better handling of commas within explanations
      parts <- strsplit(line, ",\\s*", perl = TRUE, fixed = FALSE)[[1]]
      
      if (length(parts) >= 1) {
        filename <- parts[1]
        category <- ifelse(length(parts) >= 2, parts[2], "")
        
        # Handle the explanation (everything after second comma)
        if (length(parts) >= 3) {
          explanation <- paste(parts[3:length(parts)], collapse = ", ")
        } else {
          explanation <- NA
        }
        
        filenames <- c(filenames, filename)
        categories <- c(categories, category)
        explanations <- c(explanations, explanation)
      }
    }
  }
  
  # Create and return the dataframe
  if (length(filenames) > 0) {
    data.frame(
      filename = filenames,
      category = categories,
      explanation = explanations,
      stringsAsFactors = FALSE
    )
  } else {
    # Return empty dataframe with correct structure if no data found
    data.frame(
      filename = character(0),
      category = character(0),
      explanation = character(0),
      stringsAsFactors = FALSE
    )
  }
}
lat_1956_results <- process_llm_response_to_df(politics)
write.csv(lat_1956_results, "./output/ai_classified_lat_1956_oct_1_2025.csv")
```


count the results
```{r}
lat_1956_results |> 
  count(category)

```






#Notes

Prompt guidance from Claude.ai
Suggested Prompt Structure
You are analyzing news articles to identify and categorize business issues.

BUSINESS ISSUES are defined as articles that primarily discuss:
- **Companies**: Corporate entities, their operations, or strategic decisions
- **Executives**: Business leaders, appointments, departures, or leadership actions
- **Business Activity**: Including but not limited to:
  - Product launches and announcements
  - Marketing campaigns
  - Regulatory compliance matters
  - Mergers and acquisitions
  - Partnerships and collaborations
  - Corporate strategy changes
- **Financial Dealings**: Earnings, investments, funding, stock performance, financial results
- **Industry**: Sector trends, market analysis, competitive dynamics

EXCLUSIONS:
- Labor issues (strikes, unionization, worker disputes) should be classified separately as LABOR, not business issues
- Articles that only mention a company tangentially (e.g., "Apple CEO attended a charity gala") without discussing business matters

TASK:
For each article, determine:
1. Does it contain a business issue? (YES/NO)
2. If YES, what is the primary category? (Company, Executive, Business Activity, Financial, Industry)
3. Provide a brief justification (1 sentence)



#old prompt


#used this prompt
```{r}
chat2 <- chat_gemini(
  system_prompt = "You are an academic researcher performing context analysis on selected Newsweek articles. Analyze each article and classify it based on these criteria:
  
  1. If an article contains two or more mentions of an upcoming election or electoral politics, classify it as 'politics'
  2. If an article contains two or more mentions of vote or voter registration, classify it as 'voter_turnout'
  3. If an article contains two or more mentions the economic developments, classify it as 'economy'
  4. If an article contains two or more mentions of business issues, classify it as 'business'
  5. If an article meets multiple criteria, assign multiple categories separated by semicolons
  6. If an article meets none of the criteria, classify it as 'other'
  
  Return ONLY a CSV-formatted result with exactly THREE (3) columns:
  filename, category, explanation
  
  For example:
  filename, category, explanation
  article1.txt,politics, warning about upcoming election
  article2.txt,democrat_critique, these words were critical of democrats: xyz
  article3.txt,business;politics, business mentioned three times voter turnout twice
  article4.txt,other
  
  No additional text, explanations, or summary counts."
)

# Send to the LLM
politics <- chat2$chat(combined_text_with_filenames)
```
