---
title: "Perspective coding"
author: "Wells"
date: "2025-06-25"
output: html_document
---
# Load Libraries
```{r message=FALSE, warning=FALSE, include=FALSE}

library(textdata)
library(tidyverse)
library(rio)
library(tidytext)
library(janitor)

```

## Load Data
```{r echo = F}

perspective_coded <-read.csv("./data/Perspective_coded.csv") |> 
  mutate(date = lubridate::mdy(date_cleaned)) |>   clean_names() 


```

```{r}
library(dplyr)
library(lubridate)

perspective_coded <- perspective_coded %>%
  mutate(
    date = case_when(
      # If it's already a 4-digit year format, use mdy directly
      grepl("\\d{4}", date_cleaned) ~ lubridate::mdy(date_cleaned),
      # If it has 2-digit years, fix them first
      grepl("\\d{1,2}/\\d{1,2}/\\d{2}$", date_cleaned) ~ {
        # Split and fix the year
        parts <- strsplit(date_cleaned, "/")
        year_2digit <- as.numeric(sapply(parts, function(x) x[3]))
        # Convert 2-digit to 4-digit (adjust cutoff as needed)
        year_4digit <- ifelse(year_2digit > 25, 1900 + year_2digit, 2000 + year_2digit)
        month <- sapply(parts, function(x) x[1])
        day <- sapply(parts, function(x) x[2])
        
        as.Date(paste(month, day, year_4digit, sep = "/"), format = "%m/%d/%Y")
      },
      TRUE ~ as.Date(NA)
    )
  )

```
Part 2

```{r}

perspective_coded <- perspective_coded %>%
  mutate(
    date1 = str_extract(date_bak, "^\\d{4}_\\d{1,2}_\\d{1,2}"),  # Extract YYYY_M_D pattern
    date1 = str_replace_all(date1, "_", "-"),  # Replace underscores with dashes
    date1 = as.Date(date1)  # Convert to date
  )


perspective_coded$date2 <- as.Date(trimws(as.character(perspective_coded$date_bak)), 
                                  format = "%b %d, %Y")

perspective_coded <- perspective_coded |> 
  mutate(final_date = coalesce(date, date1, date2)) |> 
  select(-date,-date1,-date2, -date_cleaned) |> 
  rename(date = final_date)

perspective_coded <- perspective_coded |> 
  mutate(year = lubridate::year(date))


write.csv(perspective_coded, "./data/perspective_coded_june_25.csv")
```


```{r}
perspective_coded |> 
  count(code) |> 
  arrange(desc(n))


```

```{r}
perspective_coded |> 
  group_by(year, code) |> 
  count(code) |> 
  arrange(desc(n))




```

```{r}
politics <- perspective_coded |> 
  filter(str_detect(code, "Political")) |> 
  group_by(year) |> 
  count() |> 
  ggplot(aes(x = year, y = n, fill = n)) +
  geom_col(position = "dodge") + 
  theme(legend.position = "none") +
  scale_x_continuous(breaks = seq(1934, 1966, by = 2))+
  labs(title = "Moley Politics in Newsweek by Year", 
       subtitle = "Extracted Text Only",
       caption = "Graphic by Rob Wells, 6/21/2025",
       y="Count of Pages",
       x="Year")

politics


```

An analysis of Moley’s Newsweek columns shows a rise in political commentary in presidential election years: Dewey in 1948, Eisenhower in 1952, and to a less extent, Nixon in 1960 and Goldwater in 1964.


Timeline of FDR criticism
```{r}

perspective_coded |> 
  filter(str_detect(code, "FDR_criticism")) |> 
  group_by(year) |> 
  count() |> 
  ggplot(aes(x = year, y = n, fill = n)) +
  geom_col(position = "dodge") + 
  theme(legend.position = "none") +
  scale_x_continuous(breaks = seq(1934, 1966, by = 2))+
  labs(title = "Moley Critism of FDR in Newsweek by Year", 
       caption = "Graphic by Rob Wells, 6/25/2025",
       y="Count of Pages",
       x="Year")


```

An analysis of Moley’s Newsweek column showed it was often critical of FDR from 1937-1939 and less so after that time period.  [perspective_coded.rmd]One explanation for the drop-off in critical tone could be the looming crisis of World War II.


