---
title: "Moley Scrape2 Dec 16"
author: "Rob Wells"
date: "2024-12-17"
output: html_document
---

f the data frame is empty after extracting the information using XPath, it means that the XPath expression "//tr[td/@title='Expand/Collapse']" did not find any matching elements in the HTML. In that case, we'll need to inspect the HTML structure of the web page and adjust the XPath or CSS selector accordingly.
Please run the script and provide the printed output so we can further investigate the issue.


```{r}
# Install and load the required packages
# install.packages("rvest")
# install.packages("dplyr")
library(rvest)
library(dplyr)
library(tidyverse)
library(stringr)
library(readr)
```


```{r}

# Read the HTML file from the URL
url <- "https://hoover.aeon.atlas-sys.com/aeon.dll?Action=10&Form=31&Value=https://voro.cdlib.org/oac-ead/prime2002/hoover/reg_084.xml"
html <- read_html(url)

# Extract the relevant information using XPath
data <- html %>%
  html_nodes(xpath = "//tr[td/@title='Expand/Collapse']") %>%
  html_nodes("td") %>%
  html_text() %>%
  matrix(ncol = 4, byrow = TRUE) %>%
  as.data.frame(stringsAsFactors = FALSE)

print("Data after extracting information:")
print(head(data))

# Assign column names
colnames(data) <- c("Category", "Subject", "Box", "Folder")

print("Data after assigning column names:")
print(head(data))

# Filter rows starting from "DIARIES AND TELEPHONE BOOKS 1931-1940"
start_index <- which(data$Category == "DIARIES AND TELEPHONE BOOKS 1931-1940")[1]
if (is.na(start_index)) {
  start_index <- 1
}
data <- data[start_index:nrow(data),]

print("Data after filtering rows:")
print(head(data))

# Remove leading/trailing whitespace from the data
data <- data %>%
  mutate(across(everything(), trimws))

print("Data after removing whitespace:")
print(head(data))

# Populate the Category column with the appropriate values
if (any(!is.na(data$Category))) {
  data$Category <- data$Category[cumsum(!is.na(data$Category))]
}

print("Data after populating Category column:")
print(head(data))

# Write the data to a CSV file
write.csv(data, "raymond_moley_index.csv", row.names = FALSE)
```



```{r}

# Load necessary library
library(stringr)

library(stringr)
library(dplyr)

# Read the text file
text <- readLines("/Users/robwells/Code/Moley/speeches_hoover_index.txt", warn = FALSE)
```

```{r}
library(stringr)
library(dplyr)

# Read the text file
text <- readLines("/Users/robwells/Code/Moley/speeches_hoover_index.txt", warn = FALSE)

# Create empty vectors to store data
box_folders <- c()
subjects <- c()
dates <- c()

# Go through the text line by line
for(i in 1:length(text)) {
  # If line contains box and folder
  if(grepl("box \\d+, folder \\d+", text[i])) {
    box_folders <- c(box_folders, text[i])
    # Get next line for subject (if it exists)
    if(i < length(text)) {
      subjects <- c(subjects, text[i + 1])
    }
  }
}

# Clean box_folders
box_folders <- str_extract(box_folders, "box \\d+, folder \\d+")

# Extract dates from subjects
dates <- str_extract(subjects, "(January|February|March|April|May|June|July|August|September|October|November|December)\\s+\\d{1,2},\\s+\\d{4}")
dates[is.na(dates)] <- ""

# Create data frame
df <- data.frame(
  box_folder = box_folders,
  subject = subjects,
  date = dates,
  stringsAsFactors = FALSE
)

# Write to CSV
write.csv(df, "Updated_moley_speeches_index.csv", row.names = FALSE, quote = TRUE)

# Print first few rows to verify
print(head(df))
```



(works but dates need fixing)
```{r}

# Combine all lines into a single string
text_combined <- paste(text, collapse = "\n")

# Create a pattern to match each entry
pattern <- "(?:box (\\d+), folder (\\d+))\\s*([^\"\\n]+?)\\s*(?=(January|February|March|April|May|June|July|August|September|October|November|December)\\s+\\d{1,2},\\s+\\d{4}|$)\\s*(?:(January|February|March|April|May|June|July|August|September|October|November|December)\\s+\\d{1,2},\\s+\\d{4})?"

# Extract all matches
matches <- str_match_all(text_combined, pattern)[[1]]

# Create a data frame
data <- data.frame(
  box = matches[,2],
  folder = matches[,3],
  subject = str_trim(matches[,4]),
  date = matches[,5],
  stringsAsFactors = FALSE
)

# Clean up the data
data <- data %>%
  mutate(
    box_folder = paste("box", box, "folder", folder),
    subject = str_replace_all(subject, "\\s+", " "),
    subject = str_trim(subject)
  ) %>%
  select(box_folder, subject, date)

# Write to CSV
# write.csv(data, "speeches_index.csv", row.names = FALSE, quote = TRUE)
# # Write to CSV
# write.csv(data, "speeches.csv", row.names = FALSE)

# Print the data frame to verify
print(data)

```


```{r}
data <- df |> 
  mutate(subject1 = subject,
         date1 = date)


# Function to extract month and year from subject
extract_date <- function(subject) {
  # Try different date patterns
  patterns <- c(
    # Full dates with month year
    "(January|February|March|April|May|June|July|August|September|October|November|December)\\s+\\d{4}",
    # Just year
    "\\b\\d{4}\\b",
    # Season and year
    "Summer\\s+\\d{4}",
    # Date ranges
    "(January|February|March|April|May|June|July|August|September|October|November|December)\\s+\\d{1,2}-\\d{1,2},\\s+\\d{4}",
    # Month range and year
    "(?:January|February|March|April|May|June|July|August|September|October|November|December)\\s+to\\s+(?:January|February|March|April|May|June|July|August|September|October|November|December)\\s+\\d{4}",
    # Years range
    "\\d{4}-\\d{4}",
    # Decade
    "\\d{4}s"
  )
  
  for(pattern in patterns) {
    match <- str_extract(subject, pattern)
    if(!is.na(match)) {
      return(match)
    }
  }
  return("")
}

# Update empty dates with extracted dates from subject
df <- df %>%
  mutate(
    date = ifelse(date == "" | is.na(date), 
                 sapply(subject, extract_date),
                 date)
  )

# Extract year from date field
extract_year <- function(date_string) {
  # Extract 4-digit year regardless of format
  year <- str_extract(date_string, "\\d{4}")
  return(year)
}

# Example usage with your data frame
df$year <- sapply(df$date, extract_year)

write.csv(df, "Updated_moley_speeches_index.csv", row.names = FALSE, quote = TRUE)

```


# Define the input text
text <- "
box 119, folder 1
Cleveland City Club Address October 15, 1932

box 119, folder 2
Rochester Chamber of Commerce Address January 16, 1933

box 119, folder 3
Columbia Alumni Address February 13, 1933

box 119, folder 4
Cincinnati Address March 17, 1933

box 119, folder 5
Radio Address on London Conference May 20, 1933

box 119, folder 6
Welfare Council Address May 23, 1933

box 119, folder 7
Liberal Conference Address September 8, 1933

box 119, folder 8
Cleveland Address October 31, 1933

box 119, folder 9
American Institute of Banking (Cleveland) Address, (?) (no text or notes) November 1, 1933

box 119, folder 10
Barnard Alumnae Association Address November 2, 1933
"
