---
title: "Compile Moley LAT articles Text"
author: "Wells"
date: "2025-06-21"
output: html_document
---

This notebook compiles 2503 newspaper articles by Raymond Moley published by the Los Angeles Times from 1942 to 1969


```{r}
#install.packages("pdftools")
library(tidyverse)
library(pdftools)
library(janitor)
```

# Compile Text into a Dataframe

## Raw text compiler 
```{r include=FALSE}
#This creates an index with the file path to the stories. And then it compiles the stories into a dataframe
#####################
# Begin SM Code #####
#####################

###
# List out text files that match pattern .txt, create DF
###

files <- list.files("./moley_lat_txt", pattern="*.txt") %>% 
  as.data.frame() |> 
  rename(filename = 1) |> 
  mutate(index = as.numeric(str_replace_all(filename, "_1_page0.txt","")))

#Join the file list to the index

#load final data if you haven't already
final_data <- rio::import("./data/moley_lat.csv") |> 
  clean_names() |> 
  rename(index = store_id) |> 
  mutate(index = as.numeric(index))

moley_lat_full_index <- rio::import("./data/moley_lat_full_index.csv") |> 
  clean_names() |> 
  mutate(date = lubridate::mdy(pub_date)) 

final_index <- final_data |> 
  inner_join(files, c("index")) |> 
  mutate(filepath = paste0("./moley_lat_txt/", filename)) |> 
  mutate(date = lubridate::mdy(entry_date)) |> 
  select("date", "year", "title", "abstract", "authors", "filename", "filepath", "index", "issn", "pages", "document_url", "find_a_copy") |> 
    mutate(year = lubridate::year(date))
head(final_index)

write.csv(final_index, "./data/moley_lat_final_index_scanned_june_21.csv")

```

#### Misc Notes:

           authors    n
1                                     Moley, Raymond 2480
2                                     RAYMOND MOLEY:    5
3                                 Moley, Raymond, Jr    4
4                                   Moley--, Raymond    4
5                    Lippmann, Walter;Moley, Raymond    2
6                  Moley, Raymond;Moley, Raymond, Jr    2
7                   Holmes, Alexander;Moley, Raymond    1
8  Lippmann, Walter; Mowrer, Edgar A; Moley, Raymond    1
9                     Moley, Raymond; Hirsch, Julius    1
10                             WITH RAYMOND MOLEY JR    1

Fact Check
final_data$dates_match <- final_data$entry_date != final_data$pubdate

final_data |> count(pubtitle) |> arrange(desc(n))

### List of Missing Files

```{r}

#38 MISSING FILES from 2547, 1.5% missing. GOOD!

missing_lat_scans <- moley_lat_full_index |> 
  anti_join(final_index, by=c("date"))


write.csv(missing_lat_scans, "./data/MISSING_moley_lat_SCANS.csv")

```




## Text compiler
```{r}
###
# Define function to loop through each text file 
###

create_article_text <- function(row_value) {
  
  #row_value is the single argument that is passed to the function
  # Take each row of the dataframe
  temp <- final_index %>%
    slice(row_value)
  
  # Store the filename for  use in constructing articles dataframe
  temp_filename <- temp$filename
  
  # Create a dataframe by reading in lines of a given textfile
  # Add a filename column 
  articles_df_temp <- read_lines(temp$filepath) %>%
    as_tibble() %>%
    mutate(filename = temp_filename)
  
  # Bind results to master articles_df
  # <<- returns to global environment
  articles_df <<- articles_df %>%
    bind_rows(articles_df_temp)
}

###
# Create elements needed to run function
###

# Create empty tibble to store results
articles_df <- tibble()
#running once to test
#create_article_text(2) 
# Create an array of numbers to loop through, from 1 to the number of rows in our index dataframe 
row_values <- 1:nrow(final_index)

###
# Execute function using lapply
# This loops through each row of the dataframe and append results to master file
###

lapply(row_values, create_article_text)

###
# Clean up articles_df and join to index dataframe
###

articles_df <- articles_df %>%
  select(filename, sentence=value) %>%
  inner_join(final_index)



```

# Clean text

```{r}
articles_df <- articles_df %>%
  group_by(filename) %>%
  mutate(row_num = row_number()) %>%
  filter(!(row_num == 1 & str_detect(sentence, "^Here's"))) %>%
  select(-row_num) %>%
  ungroup() |> 
  mutate(year = lubridate::year(date))

write.csv(articles_df, "moley_lat_text_june_21.csv")
```


```{r}
cleaned_articles_df %>%
  group_by(filename) %>%
  slice(1) %>%
  select(filename, sentence) %>%
  head(10)
```

