---
title: "Renaming Extracted Files"
author: "Wells"
date: "2025-05-22"
output: html_document
---
This code renames the extracted perspective columns so they are represented by dates and not obscure batch numbers

```{r}
library(tidyverse)
library(rio)
library(janitor)
library(googlesheets4)
```
Import the main Perspective index
```{r}
perspective <- rio::import("/Users/gizmofo/Code/Moley/matching with extract-Perspective_full_index_1967_1937.xls") |> 
  clean_names() |> 
  mutate(date_new = lubridate::mdy(pubdate)) |> 
  mutate(index_new = str_replace_all(index, ".pdf", "_page0.txt"))
```






copy and rename
```{r}
results <- perspective_final %>%
  rowwise() %>%
  mutate(
    old_path = file.path("/Users/gizmofo/Library/CloudStorage/Dropbox/Current_Projects/Moley project 2024/Perspective Columns/perspective_extracted", index_new),  
    file_exists = file.exists(old_path),
    new_filename = paste0(date_new,"_", index_new),
    # 
    new_path = file.path("./test", new_filename),
    success = ifelse(file_exists, 
                    file.copy(old_path, new_path), 
                    FALSE)
  ) %>%
  ungroup()

# Check results
print(paste("Successfully copied:", sum(results$success), "files"))
print(paste("Failed to copy:", sum(!results$success), "files"))

# Analyze failures
failed_files <- results %>% filter(!success)
missing_files <- failed_files %>% filter(!file_exists)
copy_failures <- failed_files %>% filter(file_exists)

print(paste("Files that don't exist:", nrow(missing_files)))
print(paste("Files that exist but failed to copy:", nrow(copy_failures)))

```
write.csv(results, "perspective_txt_renamed_7_23.csv")

clean missing files

```{r}
missing_files_1 <- missing_files |> 
  mutate(index_new = str_replace_all(index_new,"_page0", ""))

# Remove the rows with the problematic indices from the original perspective dataframe
perspective_updated <- perspective %>%
  # Exclude the rows that are in missing_files_1
  filter(!(index %in% missing_files_1$index))

# Bind the corrected rows from missing_files_1 to the updated dataframe
perspective_final <- bind_rows(
  perspective_updated,
  missing_files_1 %>% 
    # Select only the original columns from the original perspective dataframe
    select(names(perspective))
)

# Verify the replacement
print("Original perspective rows:")
print(nrow(perspective))

print("Updated perspective rows:")
print(nrow(perspective_final))

print("Rows with the replaced indices:")
print(perspective_final %>% 
        filter(index %in% missing_files_1$index) %>% 
        select(index, index_new, date_new))
  
```


#wrote out to disk: 
 write.csv(missing_files, "the_16_missing_perspective_scans_7_22.csv")

rename pdfs 
```{r}
results <- perspective_final %>%
  rowwise() %>%
  mutate(
    old_path = file.path("/Users/gizmofo/Library/CloudStorage/Dropbox/Current_Projects/Moley project 2024/Perspective Columns/Perspective_single_pdfs", index),  
    file_exists = file.exists(old_path),
    new_filename = paste0(date_new,"_", index),
    new_path = file.path("./perspective_pdf_renamed", new_filename),
    success = ifelse(file_exists, 
                    file.copy(old_path, new_path), 
                    FALSE)
  ) %>%
  ungroup()

# Check results
print(paste("Successfully copied:", sum(results$success), "files"))
print(paste("Failed to copy:", sum(!results$success), "files"))

# Analyze failures
failed_files <- results %>% filter(!success)
missing_files <- failed_files %>% filter(!file_exists)
copy_failures <- failed_files %>% filter(file_exists)

print(paste("Files that don't exist:", nrow(missing_files)))
print(paste("Files that exist but failed to copy:", nrow(copy_failures)))




```
 



```{r}
missing_scans <- results |> 
  filter(success == "FALSE")

write_csv(missing_scans, "missing_scans.csv")
```


Import the stratified sample index
```{r}
googlesheets4::gs4_deauth()
stratified <- read_sheet("https://docs.google.com/spreadsheets/d/1GCvfNHgEN_TP1KA6YdpBf-Bp0YdwGOeG8x9uSzjHvGI/edit?gid=1734194128#gid=1734194128") |> 
  clean_names()
```
fix date column
```{r}
stratified <- stratified |> 
 mutate(date_new = case_when(
    is.na(issue) ~ NA_character_,
    TRUE ~ str_extract(issue, "\\d{4}[-_]\\d{2}[-_]\\d{2}")
  )) |> 
  mutate(date_new = lubridate::ymd(date_new))
```

join with results

```{r}

sample_index <- stratified |> 
  inner_join(results, by=c("date_new")) |> 
  select(new_filename,  date_new, title.y, year.y, max_qda_imported, pubdate,abstract,index) |> 
  arrange(desc(date_new))

write_csv(sample_index, "sample_perspective_reading_index.csv")

```


copy to a new sample reading folder
```{r}
results2 <- sample_index %>%
  rowwise() %>%
  mutate(
    source_path = file.path("./perspective_renamed", new_filename),
    dest_path = file.path("./stratified_sample", new_filename),
    file_exists = file.exists(source_path),
    success = ifelse(file_exists, 
                    file.copy(source_path, dest_path), 
                    FALSE)
  ) %>%
  ungroup()

# Check results
print(paste("Successfully copied:", sum(results2$success), "files"))
print(paste("Failed to copy:", sum(!results2$success), "files"))

# Show any failures
failed_files <- results2 %>% filter(!success)
if(nrow(failed_files) > 0) {
  print("Failed files:")
  print(failed_files$new_filename)
}

```



NOTES


alternate attempt at renaming files
```{r}


```{r}
# Get the full path to the perspective_extracted directory
base_dir <- getwd()
perspective_extracted_path <- file.path(base_dir, "perspective_extracted")
perspective_renamed_update_path <- file.path(base_dir, "perspective_renamed_update")

# Ensure destination directory exists
dir.create(perspective_renamed_update_path, showWarnings = FALSE, recursive = TRUE)

# Function to find the actual file path
find_file_path <- function(index_new, base_path) {
  # Possible variations of the filename
  possible_names <- c(
    index_new,
    sub("\\.pdf$", "_page0.txt", index_new),
    sub("\\.pdf$", ".txt", index_new),
    paste0(index_new, "_page0.txt"),
    paste0(index_new, ".txt")
  )
  
  # Try each possible filename
  for (filename in possible_names) {
    full_path <- file.path(base_path, filename)
    if (file.exists(full_path)) {
      return(full_path)
    }
  }
  
  # If no file found, return NA
  return(NA_character_)
}

# Exclude 'na' entries and capture all files
results <- perspective %>%
  filter(!is.na(date_new) & 
         !is.na(index_new) & 
         index_new != "na" & 
         index_new != "na_page0.txt") %>%  
  rowwise() %>%
  mutate(
    # Find the actual file path
    old_path = find_file_path(index_new, perspective_extracted_path),
    
    # Check file existence
    file_exists = !is.na(old_path) & file.exists(old_path),
    
    # Create new filename
    new_filename = paste0(date_new, "_", 
                          # Remove .pdf if present
                          sub("\\.pdf$", "", index_new), 
                          # Ensure _page0.txt suffix
                          ifelse(grepl("_page0\\.txt$", old_path) || 
                                   grepl("\\.txt$", old_path), 
                                 "", "_page0.txt")),
    
    new_path = file.path(perspective_renamed_update_path, new_filename),
    
    # Attempt to copy
    success = if_else(file_exists, 
                      file.copy(old_path, new_path, overwrite = TRUE), 
                      FALSE)
  ) %>%
  ungroup()

# Verify paths
print("Sample old paths:")
print(head(results$old_path))
print("Sample new paths:")
print(head(results$new_path))

# Check results
print(paste("Successfully copied:", sum(results$success), "files"))
print(paste("Failed to copy:", sum(!results$success), "files"))

# Analyze failures
failed_files <- results %>% filter(!success)
missing_files <- failed_files %>% filter(!file_exists)
copy_failures <- failed_files %>% filter(file_exists)
print(paste("Files that don't exist:", nrow(missing_files)))
print(paste("Files that exist but failed to copy:", nrow(copy_failures)))

# Detailed debugging
if(nrow(failed_files) > 0) {
  print("Failed files details:")
  print(failed_files %>% select(index_new, old_path, new_path, file_exists))
}

# Verify directory contents
print("Files in source directory:")
source_files <- list.files(perspective_extracted_path)
print(length(source_files))

print("Files in destination directory:")
dest_files <- list.files(perspective_renamed_update_path)
print(length(dest_files))

# Optional: Print first few failed files for inspection
if(nrow(failed_files) > 0) {
  print("First few failed files:")
  print(head(failed_files$index_new))
}
```

```



```{r}
# Check for duplicate dates
duplicate_dates <- perspective %>%
  filter(!is.na(date_new) & !is.na(index_new) & index_new != "na_page0.txt") %>%
  count(date_new, sort = TRUE) %>%
  filter(n > 1)

print(paste("Number of dates with duplicates:", nrow(duplicate_dates)))
print("Top duplicate dates:")
print(head(duplicate_dates, 10))

# Let's test with a small sample and see exact error
test_sample <- perspective %>%
  filter(!is.na(date_new) & !is.na(index_new) & index_new != "na_page0.txt") %>%
  slice(1:3)

# Test each file individually
for(i in 1:nrow(test_sample)) {
  row <- test_sample[i,]
  old_path <- file.path("./perspective_extracted", row$index_new)
  new_path <- file.path("./perspective_renamed", paste0(row$date_new, ".txt"))
  
  cat("Testing file", i, ":\n")
  cat("Source:", old_path, "\n")
  cat("Destination:", new_path, "\n")
  cat("Source exists:", file.exists(old_path), "\n")
  
  if(file.exists(old_path)) {
    result <- tryCatch({
      file.copy(old_path, new_path, overwrite = TRUE)
    }, error = function(e) {
      cat("Error:", e$message, "\n")
      return(FALSE)
    })
    cat("Copy result:", result, "\n")
  }
  cat("---\n")
}
```

